%@+leo-ver=4-thin
%@+node:gcross.20081101122204.4:@thin story.tex
%@@language latex

\documentclass[showtrims,b6paper,draft,10pt]{memoir}
%\documentclass[showtrims,b6paper,10pt]{memoir}
%\documentclass[showtrims,draft,10pt]{memoir}
%\documentclass[final,10pt]{memoir}
%\documentclass[showtrims,draft,a5paper,10pt]{memoir}
%\documentclass[showtrims,draft,10pt]{memoir}

%\setstocksize{6.88in}{4.20in}
%\settrimmedsize{6.88in}{4.20in}

\setlrmarginsandblock{.525in}{.4in}{*}
\setulmarginsandblock{*}{.5in}{1.5}
\checkandfixthelayout

\usepackage{srcltx}
\usepackage{times}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{flafter}

\begin{document}

\newcommand{\timeskip}{\begin{center}* * *\end{center}}

%@+others
%@+node:gcross.20081115104035.2:Graveyard
\begin{comment}

%@+others
%@+node:gcross.20081115104035.3:Christina runs into her dragoneer, take 1
He took a deep breath, and then addressed her nervously.  ``Christina, Arthur is terrified and wants to leave as soon as possible.''

``Fine!  There is nothing you can do here to help, so head on out.''

``But we ca--- wait, you are telling us to leave?''  he said, in

``Of course I am telling you to leave!  But make sure he takes on as many people as he can.''

``Wait, what about you?''  he asked.

Christina held up her sword dramatically. ``Don't worry, I--'' Christina started to say, but then quickly interrupted herself as she thrust her sword behind her in a slashing motion.  The dragoneer looked confused.

She turned around.  There was nothing behind her.

``Oops, nevermind about that, just getting some practice is all.  Anyway, don't worry about me, I can take care of myself.  Now if you will excuse me, I have people to rescue, so farewell!''  she said, running off.
%@nonl
%@-node:gcross.20081115104035.3:Christina runs into her dragoneer, take 1
%@+node:gcross.20081101130025.10:Christina walks to meet the boss (Background on the Order), take 1
Christina was not looking forward to meeting her boss, Bill, that morning.

The campus was designed so that the dormitories were on the opposite side from the main hall, where the briefings and other business occured.  There was a reason for this;  it meant that every time a hero walked from the drom to the hall, he or she had to pass through the memorial ground in the center of the campus, and nobody could walk through this ground without being moved and inspired.

The most prominent memorial was the great statue in the middle of the ground of Patrick Smith, the man who lead the First Heroes in overthrowing King George, the infamous last of the kings who had decided that oppressing his subjects was simply more `fun' than serving them.  This, however, was not why he was honored, for many heros had defeated great enemies, but no other had their statue in this ground.  What made Patrick special was that after leading the First Heroes to overthrow the King, in the moment when the people had been willing to crown him their ruler in their stead, he refused the honor and instead created a parliamentary democracy to govern the land.  He and the First Heroes together founded the Order of Heroes, and by his insistence it was deliberately made subservient to the parliament;  on the platform below his statue is carved the calling of the Heroes of the Order:  ``We fight to protect, not to rule.''  His figure is protrayed on one knee, with a sword held high in one hand and a child cradled against him in the other.

If anyone had doubt in the commitment of the Order in carrying out its mission over the last three hundred years, it would be immediately dispelled by the plain stones surrounding the statue -- stones filled with names, hundreds of names, of the heroes who had died in service.  Every time Christina walked past the stones, she would reach out and touch some of the names.  No woman's name appeared on the stones, and in a way she was glad of this;  since she had been the first woman admitted to the order, if a name were to appear on the stones in the near future it would be her own!

She continued quietly on her way to her commander's office, sobered both by the memorial ground and also by thoughts of the briefing she was going to have to give him shortly.

\timeskip

%@-node:gcross.20081101130025.10:Christina walks to meet the boss (Background on the Order), take 1
%@-others

\end{comment}
%@nonl
%@-node:gcross.20081115104035.2:Graveyard
%@+node:gcross.20081101122204.2:Story
%@+node:gcross.20081101122204.5:Chapter 1: The Puzzle Master
\chapter{The Puzzle Master}

%@+node:gcross.20081101122204.3:Christina forgets her lockpick
The guard named Marv, leaned casually next to the door, chewing nicotine free tobacco.  “You know Joe,” he grumbled.  “It seems like we spend all of our lives alternating between standing here conscious but bored, or unconscious after some hero arrives and knocks us out.  Ever feel like we were meant for something more than this?”

The other guard started to reply, but then he immediately alternated to the latter of the two states as Christina gave him a quick kick to the head.

``Dammit,'' shrieked Marv as he attempted to quickly draw his sword.  ``Not ag--''  He didn’t get to finish his sentence, but dropped to the floor instead.

Christina fished around Marv’s pocket for the key to the door, and let herself in.  She may have had a universal lock-pick on her, but there was always a certain satisfaction to using a key you had won for yourself.

She entered and found herself inside a chamber.  The door slammed close behind her as a voice boomed, ``You must now prove that you are the Master by solving a crossword puzzle of such difficulty that only the genius of the Master himself could pass.  Fail, and your body shall be reduced to ashes.''  A set of squares faded on the wall to her left, and writing appeared on the wall to her right.  She walked up to the writing and read through it.  It would require someone with encyclopedic knowledge to figure it out.

Happily, she had just re-memorized the encyclopedia that morning.

``You have thirty minutes to complete the puzzle,'' the voice boomed.  Christina shook her head;  the Puzzle Master couldn’t possibly be as smart as he thought he was if it really took him a whole thirty minutes to solve his own puzzle.  She walked to the other side of the chamber, saying a silent prayer for the piles of ashes that lay next to it, picked up the chisel and hammer, and systematically completed the puzzle in less than ten minutes.

``Welcome, Master!''  the voice boomed as both doors opened.  She smiled with satisfaction as she walked through and entered the treasury.

A large vault stood before her;  on the inside of this vault lay all the treasure which the Puzzle Master had accumulated from several years of pillaging.  All she had to do now was open the door, load it into her weightless infinite bag of holding, and return home.

She smiled.  This was almost too easy.  She reached into her left pocket for her universal lock-pick.

It wasn’t there.

``Oops, I can never remember which pocket I put that thing in,'' she thought to herself as she reached into her right pocket.

It wasn’t there, either.

She cursed, quickly fumbling through the rest of her pockets.  She then had a vision of the lock-pick sitting on her desk as she left her home a week ago...

Oh god, not again.

She screamed and kicked at the door a few times just to see it would bulge.  Her foot hurt now, and her morale hadn’t improved.  In a deep funk, she started to make her way out of the fortress.

Marv had regained consciousness by now, and was rubbing his temple as she left the Puzzle Chamber.  ``Wait, did you really just come all this way, simply to forget you lock pick and get stuck?''  He looked at her, and started to laugh, ``Oh, now I recognize you.  You’re Christina, aren’t you?  Man, I’ve heard stories, but to actually see how stu--'' His laughter came to an abrupt end as his body slammed into the wall.

She glared at the other guard.  “Do you have anything to say?”

His face paled.  Unlike Marv, he had also heard the stories of her legendary temper.  Mollified, he asked  ``Umm, Miss, if you’re leaving anyway, could we please have our key back?  The Master gets really mad at us when we lose it...''

She rolled her eyes, and threw the key at him.  It knocked him in the forehead and he was down again.

\timeskip
%@-node:gcross.20081101122204.3:Christina forgets her lockpick
%@+node:gcross.20081101130025.1:Christina leaves the fortress
She sulked as she made her way out of the fortress.  Unfortunately, nobody else was stupid enough to mock or harass her on the way out, so she didn’t get any other opportunities to take out her frustration on someone.

Her horse was waiting for her outside.  She got on it and started making her way back to the village.  She grimaced in anticipation of what was to come.

\timeskip

%@-node:gcross.20081101130025.1:Christina leaves the fortress
%@+node:gcross.20081101122204.6:A unwelcome waiting committee
At least the crowd awaiting her return this time was a little smaller than usual, but it was still there.  As she entered the town, they started cheering, ``Hooray!  She has returned victorious from the Puzzle Master!''    They were half right, but only half.  They quieted as she made her way to the center of the town, where a platform had been set up for her to make a speech.  They waited for her to mount it, but instead she just kept riding past.

Some caught on right away, but others were confused.  ``Why is she not making a speech proclaiming her victory?'' they asked themselves, as she made her way to the town inn.  ``Could it be...''

She parked her horse in the stables and went up to her room.  She quickly packed up the remainder of her things for travelling, gave the last of her money to the innkeeper to pay for her stay, and made her way to the exit.  On her way out, a child eagerly shouted, ``How much treasure did you get from him?'' before his mom hushed him up and gave Christina a look of sympathy.  Christina shook her head, and started making her way out of town.

Thankfully, most of the crowd had dispersed by this time, though the podium remained as a monument to her failure.  One man was waiting by the gate for her, and jeered as she rode by. ``You damn heroes have been taking our money for years to support your adventures, and now that you finally get around to taking care of us you accomplish absolutely nothing!''  She just hung her head as she made her way out.

\timeskip
%@-node:gcross.20081101122204.6:A unwelcome waiting committee
%@+node:gcross.20081101130025.2:At the bar
Christina started on the long ride home.  Unfortunately, she didn't have any money to pay for inns or food;  she had been given only enough to get her to the Puzzle Master, under the assumption that she would be able to use the treasure she got from the castle to fund her way back.  It thus took her twice as long to return home as it had for her to make it out here, since she had to take time to hunt and gather to feed herself, and to set up camp and night.  She was good at these things, but this time she took no pleasure in them.

After two weeks of (unfortunately) uneventful travelling, she finally made it back to her home town.  There was enough daylight left that she had enough time to drop off her stuff at her room in the barracks, return her horse to the stables, and make her way to the town pub.  She needed to get drunk as quickly as possible, and decided that was worth taking the risk that people would actually see her.

Happily, the place was not packed.  She sat down at the bar.  The bartender walked over to her with a look of concern, but Christina just told her, ``I want a pan-galactic gargle blaster.  No; on second thought, make that a double.''

As Christina nursed her drink, she started to look over the other faces at the pub.  She was hoping to see her close friend Homer, but he was not here.  She took a big swallow, and then looked up.  A man was staring a her;  a very handsome one.  She locked eyes with him, and her heart leapt.  Could it be... was this the one?

He started to make his way towards her, his eyes locked into hers, and it was clear that they were both thinking the same thing.

She nerviously brushed through her hair to fix herself up.  People were always trying to convince her that there was no such thing as ``love at first sight,'' but here she was experiencing it at last!

She continued to stare into his eyes as he approached, and she started to greet him... as he walked straight past her and started talking to the girl behind her.  ``Your eyes... I have never seen anything like them,''  Christina watched him tell the girl, as they gazed at each other, completely oblivious to anything else.  He took her hand and kissed it.  ``It is warm in here.  Would you care to take a walk outside with me to cool off?''  ``I would love to,'' she replied, smiling.  He took her arm, and they left the pub.

Christina slumped.  Not again, she thought to herself.  I mean, honestly, what were the odds that this would happen to her five times in a row?  Was she really naive to think that the guy was actually staring into her eyes, this time?

She felt an arm wrap around her.  ``Hey buddy,'' a man said to her.  ``I saw what happened.  You really have the worst luck with these things.''

She gave Homer a smile -- small, but warm -- as she pressed herself against him for a moment.  The two of them had started their hero training together, and had developed a close friendship over the years.  ``This really isn't my day;  or my month, for that matter,'' she told him.

Homer looked at her with concern.  ``What happened this time?''

``So, I made it all the way into his fortress --- and really, you should have seen me!  He had no less than seven gangs of ninjas waiting for me, each versed in a different martial arts style in the hope that one of them would be able to take me down.  Of course, in his arrogance he gave them nearly all of the keys to his castle so as I took each one down it was easy as pie to make my way around.  And his puzzle chambers... I mean, honestly, who \emph{couldn't} solve the differential equation $dz=\frac{1}{3}x^2\,dx+\frac{1}{3}y^2\,dy$ in their head?  It's basic integration!  And, god, he keeps re-using so many of his crossword clues that I stopped having to even think about half of them...''

``And then,''  Homer asked?

``And then I realized that I had forgotten the stupid lock-pick that I needed to get into his vault.  Honestly, I feel so stupid...''

``You're not stupid, Christina, just a little absent minded is all.''  He took a deep breath.  ``You know, I really didn't want to bring this up, but maybe it is time that you thought about whether this is really the right line of work for you...''

She glared at him.  ``You're right, that is a very bad point for you to bring up.''

Homer continued.  ``Seriously though, Christina.  You are good at so many things.  You fight like a human tornado and you absorb and regurgitate knowledge like a master scholar.  But to be a hero requires more than these things;  you need to have the ability to get \emph{all} of the details right, not merely most of them, and if you can't do that then you are just being a danger to yourself.  There is a reason, after all, that are not allowed to have partners anymore.''

She flushed and pulled away from him.  ``I choose not to have partners because they keep slowing me down and getting in my way!  How can I help if they keep putting themselves in front of my leg when I am in the middle of kicking people?'

``They were trying to help you...''

``Well maybe I don't need any help!'' she shouted at him.  Then she relaxed and slouched.  ``Sorry, I know that you are just trying to help.''

``No, the fault is mine;  I shouldn't have brought it up.  Here, I'll buy you a drink to make it up to you,'' Homer graciously conceded.

She smiled at him.  ``Oh, stop it, you know that I was being unreasonable and are just too nice to say it.  You really treat me too well, you know that?''

He returned the smile.  ``Hey, what other hero can I go picking up guys with?  Oops, another sore point,'' he said as she slouched again.

``Why do the guys always go for the girl next to me, Homer?  Am I really so ugly?''

Homer sighed.  ``Of course not, Christina.  Perhaps it's just that you can come across as being a little, well, intimidating at times?''

``I AM NOT INTIMIDATING!''  she shouted as she slammed her hand onto the bar.  Unfortunately, the hand did not stop at the bar, but made its way all the way through as the bar was split into two pieces.

Homer tried to avoid laughing as Christina blushed.  She sheepishly muttered, ``You know, maybe there is such a thing as doing too many wood breaking drills...  I really need to get myself out of the habit of doing this.''

The bartender walked over and shook his head.  ``I guess I'll be billing this to the Order as well?''

Just what I needed, Christina thought to herself, something else for the boss to chew me out over.  ``Yes,'' she replied.

Homer stood and patted Christina on the back.  ``I think that it's time for us to be going home.''

She sighed, stood, and followed him out the door. 

\timeskip
%@-node:gcross.20081101130025.2:At the bar
%@+node:gcross.20081101130025.3:Homer walks her home
Since Homer and Christina lived in the same barracks, they walked home together.  Homer's room was before Christina's in the hallway, but he walked past it to escort her to her door.  She appreciated the gesture, but was embarassed when she opened her door.  I don't just fight like a tornado, she thought to herself, I live like one too.

Homer looked at the mess inside, and then at Christina inquisitively.  ``I was a little hurried packing to leave, so I tore my room apart.''

He smiled, kindly. ``Well then, let's put it back together.''

``Aww, that really isn't neccessary...'' Christina started to protest.  Homer raised his hand.  ``What are friends for?  You've helped me deal with worse, after all,'' he replied entering the room.

She smiled and followed him inside.  They proceeded to pick up the items scattered across the floor and put them away.  Homer picked up a bag on the floor and asked her,  ``Tell me you didn't leave your infinite bag of holding here as well while you were out adventuring?''

She laughed, ``No, thankfully, at least I remembered that.  What you're holding is actually just a bag that I use for shopping that's decorated to look like it.  I would love to use my infinite bag of holding all of the time, but unfortunately as you know it can only hold treasure and not practical items like armor or anything else I'd actually want to buy.  Of course, most of the merchants don't know that so they just assume that I am there to buy a whole lot and give me very good service while I am there.''

``You still buy your own armor?'' Homer asked as he put the bag away in the top drawer.  ``I thought that the Order had just finished redesigning it so that it can fit women now.''

``It's true that the new armor is finally, shall we say, `anatomically correct', but it still lacks style, and if you can't have a little style then what's the point of being a hero?''

``Point,'' Homer chuckled, and the two of them continued to chat the time away as they brought the room back to a state of order.

``Thank you so much for taking care of me tonight, Homer,''  Christina told him warmly as he left the room.

``My pleasure,'' he replied, turning to face her while standing in the doorway.  ``Heck, it is the least I can do after you spent an entire month taking care of me after my ex dumped me.''

She ran up to him and gave him a hug, and then they both went to bed.

\timeskip

%@-node:gcross.20081101130025.3:Homer walks her home
%@+node:gcross.20081108185724.7:The Expositionary Monument
Christina was not looking forward to meeting her boss, Bill, that morning.  However, her thoughts on this were interrupted as she approached the monument.

In order to give the heros a daily reminder of what the order stood for, there was a memorial ground in between the barracks and the main office, forcing them to walk through it on the way to do business.  In the middle of the ground stood a statue dedicated to Patrick Smith the Great, the founder of the Order.  This alone would have been enough make him worthy of honor, but the full story was even more inspiring

Patrick had lead the First Heros to overthrow the last of the kings, King George, after the former king had decided that oppressing and terrorizing his people was more fun than protecting them.  After he had won, the people wanted to crown him king in replacement, but Patrick refused.  Instead, he lead an effort to build a new institution to govern in the place of the king, a parliament filled by respresentatives elected by the people.  Rather than giving the Order power in the government, he founded it as a servent of the body, ready to be called upon to protect the people.

Of course, democracies are messy things.  The First Parliament did a horrible job of governing, even if it was a little better than many of the worst kings, and many people why he was supporting such an organization and did not move to take control himself.  He replied, ``I know that this system of government is imperfect, but no system will be perfect and this will be better on average than any other.''  Then someone asked, ``But why keep it, when you could have the chance to take over and be a perfect ruler?''  He laughed, and replied, ``I am hardly perfect, there is no such thing as perfect in this world, and it would be a fool's errand to sacrifice the good in a vain attempt to attain it.''  He then continued to speak his most famous words, which were carved on the side of the podium underneath his statue:

\begin{center}
\textsc{We fight for the good, not for the perfect.}
\end{center}

There were certainly many times after Patrick's death when the Order had been tempted to take matters into its own hands, but they had so much respect for his honor and wisdom that they kept to his words and never allowed themselves to break the government in order to save it.  This may seem like a silly worry now when these institutions are so deeply rooted, but at the time they had just emerged from an era of Might makes Right and so it was very difficult to restrain when one had the power to force one's way.  But they did, and the world was a better place for it.

And in case this was not enough, the statue itself gave further reminder to the meaning of the hero's call.  Unsurprisingly, in Patrick's right hand was a sword held high;  but in his right hand, he held a child close to him, adding emotional impact to the words carved on the opposite site,

``Never forget who it is that you serve, and why.''

Since all who passed this memorial were exposed to the meaning of the Order and its history, it was often called the ``Expositionary Memorial.''

As Christina started walking away from it, her thoughts turned back to the present.  She was not looking forward to what her commander, Bill, would have to say to her.

\timeskip

%@-node:gcross.20081108185724.7:The Expositionary Monument
%@+node:gcross.20081101130025.4:Meeting with the boss
As expected, her commander, Bill, was less than pleased.

``So let me get this straight... you made it all the way into the vault -- something that has eluded many of our best heros and reduced them into ashes -- and then you couldn't go in because you forgot your lock-pick.''

Christina just sat in silence, her head hung low.

Bill shook his head.  ``Listen, Christina, the people don't pay us to go adventuring just for the fun of it!  We are paid to right wrongs, to return the money that was plundered to them by villains.  I don't know how much longer we can support you if you keep this up.''

Shock entered Christina's face.  She was aware of how disappointed Bill had been of her, but this was the first time he brought up firing her.  She looked up,  ``Give me another chance, Bill, I swear to you that this time I will get it right.''

``Happily, as it turns out,'' Bill replied, reaching into his desk, ``I do have another mission for you.  It's a tough one, though, but quite frankly if you can't do it, then nobody can.''

Christina perked up.  ``Thank you for having faith in me, Bill!''

Bill snorted.  ``I am not saying that I think you will be able to pull this off, just that if you can't then it is unlikely that anybody else could have.  For all of your forgetfullness and inability to actually complete missions, you are still the smartest, toughest, and fastest hero we have on the rolls.  And so even though I don't think that you will succeed, I would hate to see us not even try and at least I can be reasonabily confident that you won't get your soul eaten.''

Christina's eyes widened.  ``You don't mean...''

``Yes, Christina, I do.  Although the Soul Eater's magic is powerful enough to let him keep his lair outside this world most of the time, even he cannot prevent it from surfacing from time to time, and our wizards have calculated that it will surface in the middle of the ocean again three days from now, and remain here for twenty-four hours before returning to the Aether.''

``Three days?  That isn't nearly enough time...''

``We have hired the service of a dragoneer to drop you off just at the start of the twenty-four hour window and to pick you up at the end.  That might not seem like a lot of time, but happily the Soul Eater, like every other villain, is in some respects his own worst enemy.  He believes that no one would dare to actually infiltrate his lair during this window, so he has not put up as many traps as you are used to having to deal with --- at least, that is what our latest intelligence is on the subject.''

``How recent is that intelligence?''  Christina asked.

``One hundred years old, dating from the last time he surfaced,''  Bill answered.  ``Should I bother asking you whether you are up for this mission?''

Christina slammed her hand against the desk and declared, ``Of course I am up for it!  The dangers might be great, but the glory shall be greater still -- the infamous Soul Eater is about to meet his match!  And, oh, sorry about your desk...''  she finished sheepily, brushing small pieces of wood from her hand.'

``It's okay,'' Bill sighed, staring at the two pieces of wood where his desk had been.  ``I have finally learned by now to never have a meeting with you using my `good desk', so this was a cheap one made soley for this occasion.''  He turned his eyes towards her and looked sharply.  ``But though we may be well funded, it's not like Order is made of money, Christina.  You would do well to remember that.''

A new man entered the room.  He smiled at Christina.  ``Oh, hey, great to see you again!  How did my universal lock pick work?  Were you able to use it to enter the vault?  I spent a lot of time working on that one.''

``No need to talk about that just now, Marcus, '' Bill replied gruffly.  ``It suffices to say that the adaquateness of your lock-pick was not responsible for the failure of her mission.  Why don't you take her down to the lab to show her the new gadgets you have enchanted for her next mission.''

``Oh, the mision failed?  What happened?  Was it the sleeping pills I gave you?  I tested them on our lab dragon to make sure that the spell was strong enough.  Believe me, he was not to happy about...''

``Marcus!''  Bill shouted.

``Oh, right sir.  Well, let's get going then,'' he said to Christina.  She stood and followed him down to his lab.

\timeskip

%@-node:gcross.20081101130025.4:Meeting with the boss
%@+node:gcross.20081101130025.5:Marcus shows Christina the new toys
``You'll love what we have for you this time!'' Marcus told Christina with excitement as they made their to the lab.

Despite being in a horrible mood, Christina couldn't help but smile.  Marcus's enthusiasm never cease to be infectious.

``This mission you are going on had some unusual challenges for us, but happily we solved every one of them!  Ah, here we go,'' he said, as they entered the lab.

Christina gasped.  A large, beautiful cloth stretched before her, with ropes handing from four of the corners.

Marcus grinned at her reaction.  ``Do you like it?  We call it a `fall-breaker'.  The cloth was woven to be very, very light, but thick enough that it actually will trap air under it and allow you to glide to the ground after you jump off the dragon.''

Surprised, Christina asked,  ``I am jumping off the dragon?''

``Oh, Bill hadn't told you that part yet?  Yes, unfortunately the dragon is going to be very spooked by the island and so it won't be able to land you there.  It will bring you in pretty close, and then you will jump off wearing the fall-breaker and glide down to the island.''

``There is no way you are testing that thing on me!''

``Don't worry Christina, it has already been tested.  I jumped off the top of the town clock tower a couple of times with it myself, and the second time I didn't even break any bones!  But enough about the fall-breaker.  You might now be wondering how it is that you are going to get off the island if the dragon will not be landing to pick you up.''

Christina choked.  ``Actually, it hadn't even occured to me to worry about that until you mentioned it.''

Marcus beamed.  ``That is exactly why you should be glad to have genuiuses like us thinking about these things for you!  Look, see this ball here,'' he said, picking up a small ball with a rope attached to it, and holding it before her.  ``Just squeeze this three times, and it will inflate to become gigantic,'' he said.  He squeezed the ball, and as promised it grew until it was larger than Marcus.  It started to float to the ceiling, and he held onto the rope and allowed it to lift him.  ``See?  We call this a `float ball', and it will let you fly back up to the dragon when you are finished!  Umm... except we haven't worked out how to make it gently deflate it yet, so could you catch me when I let go of the rope.''

Christina couldn't help laughing.  ``Of course, Marcus,'' she replied.  She held out her arms and caught him as he returned to the ground.

``Thank you!'' Marcus said, regaining his composure.  ``But this isn't all we have for you.  Now, what is the most annoying problem that heros have after they have defeated their villain?''

Christina was embarassed to reply, ``I actually don't have much practical experience with that, so...''

``Convincing him to order his minions to load up your infinite bag of holding with his treasure!  After all, there is usually so much of it that it would take at least a day to load it all yourself.  Add in the fact that the Death Eater is a creature of the Aether making him very difficult to hurt directly, and it would normally be impossible to convince him to do anything at all for you.''  He paused for dramatic effect.

Christina smiled, and asked, ``But?''

``But since he is made of the ether, we can actually \emph{force} him to work for us by touching him with this stone,'' he answered with enthusiasm, holding a glowing red sphere the size of his palm.  ``This was actually a pet project of mine that I have been working on in my spare time for the last few years;  I never thought I'd get the chance to actually see it in use!''

Christina knew better than to ask, but nervousness got the better of her.  ``And you are sure this works?''

``Of course!  We summoned several spirits of varying strengths and sizes to test it and it worked on all them.''

Christina thought for a moment.  ``Could you mount it on a staff for me?''

``Certainly!  We'll call it your Sceptre of Power,''  Marcus beamed.  ``Anyway, this is all we have for you for his mission.  Here are the operating instructions for all of them,'' he said, handing her several rolls of parchment.  ``And the two rolls on the bottom contain all the details of the mission.''

``Thank you,'' Christina replied sincerely as she took the scrolls.  ``I need to start reading through all this right now, since I will be leaving really soon.''

``Of course.  Let us know how everyone worked!''

``Will do, Marcus,''  Christina said to him as she left the room.

\timeskip


%@-node:gcross.20081101130025.5:Marcus shows Christina the new toys
%@+node:gcross.20081103183256.2:Christina prepares for the mission
The flight to the island was going to take two days, so Christina had only a single day to get herself ready for the mission.  She started by reading through all of the scrolls several times to make sure she understood how to use the new equipment.  To make sure she was comfortable using it, she managed to get her hands on extras that she spent a couple of hours training with.  She was surprised at how manueverable the `fall-breaker' was.  There were some ropes that let her turn left or right, and others that let her control the speed of her descent.  By tugging on the ropes, she could accurately steer herself to a particular spot on the ground;  just in case, though, she first borrowed many, many bales of hay and set them up over a wide area.

As she was practicing, she could hear the sounds of a crowd cheering in the distance.  It spurned her to work harder to prepare -- pretty soon, that would be \emph{her} crowd cheering her own triumphant return!

Eventually she felt comfortable with everything.  The day was almost done, so she made a list of everything she needed and carefully went through it as she packed everything up.  She really wanted to tell Homer where she was going, but he was away that night, so she instead made sure she got an early night's sleep.
%@-node:gcross.20081103183256.2:Christina prepares for the mission
%@+node:gcross.20081101130025.6:Christina mounts her dragon
The next morning, Christina woke up, picked up her things, and started making her way to the dragonport.  As she opened the door to go outside the barracks, she was greeted by the sight of a massive crowd which suddenly burst into cheering.

A tear crossed her eye.  She had heard of heroes who were successful and so loved that they had crowds who actually cheered their departure as well as their arrival, but she had never believed that there would ever be a crowd cheering her on!  She opened her mouth and started to say something as she felt a hand on her shoulder.  ``Pardon me, Christina, but you are blocking the door.''  Then Christina realized something: it was not her name that the crowd was cheering.

``Ba-rack!  Ba-rack! Ba-rack!'' they all shouted as Barack edged her way past her and walked down to the crowd.  Christina watched as they followed him away from the barracks.  The tear was still in her eye, but for a different reason now.

She clenched her fists.  ``Pretty soon, they \emph{will} be cheering for me!''  She started making her way down to the dragonport, in the process running through her mental list of things to bring.  `Fall-breaker'... check.  Float ball... check.  Sceptre of Power... check.  Universal lock-pick... check.  Raw meat for the crocadiles... check.  Infinite bag of holding... oops!  She mentally kicked herself:  how could she have forgotten \emph{that}?  She ran back to her room, opened her top drawer and grabbed her bag, and headed back out.

As she made her way to the dragonport, she saw a crowd waiting there for here.  So she did have fans!  She started to grin, until she saw the signs.

STOP BURNING OUR MONEY TO FUND YOUR ADVENTURES!

MAKE PEACE WITH OUR ENEMIES, NOT WAR!

THE `ORDER' ONLY BRINGS CHAOS!

Oh, god, why was she always the one who drew the pacifists?  She pushed her way through them and made her way to the dragon.  She head someone shout,  ``It is no wonder that our enemies pillage us with the way you heros treat them!''

Christina fumed.  She turned to face the crowd, and shouted ``Do you have any idea who it is I am about to fight?  No one less than the Soul Eater himself!  Do you know what he does?  He comes to the Earth and not only steals their money, but eats their living souls!''

``Maybe he would stop picking on us if you heros stopped bothering him!''

Christina groaned.  ``We haven't ever pulled off a successful attack on him...''

``Yeah, but you keep trying!''

``Yes, but keep in mind,''  Christina shouted back, ``that this is the SOUL EATER.  He needs to feed on souls in order to live.  Even if he stopped bothering us, he has \emph{farms} where he raises \emph{human beings} to feed his unearthly hunger!  The least we can do is cause him a little pain in return.''

``His internal affairs are not our problem!''

Christina flushed with rage, and was about to say more when the dragoneer called to her, ``Come on!  We barely have enough daylight to make it our next stop as it is.''  She took a deep breath, tuned around, and started to climb onto the dragon's back.

``Besides, how do we know that he even likes eating souls?''  someone shouted.  ``For all we know, he hates eating souls and just does it to live!  Does living according to his nature give us the right to attack him?''

``If it turns out that he gets a stomach ache every time he eats a soul, I will absolutely collapse into tears,'' replied Christina sarcastically;  many of the crowd laughed in response as the dragon took to flight.

\timeskip
%@-node:gcross.20081101130025.6:Christina mounts her dragon
%@-node:gcross.20081101122204.5:Chapter 1: The Puzzle Master
%@+node:gcross.20081108185724.9:Chapter 2: The Soul Eater
\chapter{The Soul Eater}

%@+node:gcross.20081101130025.7:Flying; conversation with a dragon
As the dragon took off into the air, Christina marveled at the sight below her.  She was incredibly lucky to have the opportunity to travel this way;  dragons were so expensive that only the very rich could afford to use them.

A few moments later, she had a second revelation:  she absolutely hated flying!  It was like experiencing the discomfort of horse-riding and the sickness of sailing at the same time.  She closed her eyes in the hope that this would make it better, and when it failed to do so she unloaded her breakfast to the ground below.  She was grateful that at least the dragoneer hadn't seemed to notice, since the rush of wind at the speeds at which they were travelling made it impossible to hear anything.  She sighed, and held on.

Eight agonizing hours later, they arrived at their destination, the town of Leighover.  Flights very frequently made stops here, so there was a landing area prepared for the dragon, complete with several cows for snacks.  The dragon landed in the middle of a field, allowed the pilot and his passenger off, and then immediately started chowing down on the cows.  Christina and the dragoneer made their way to the inn, where Christina -- who was starving, as she was not able to eat anything while flying -- ate nearly as much as the dragon, and then collapsed into bed.  Who would have thought that flying could be so exhausting?

The next day was much the same;  she didn't feel as bad this time, though -- perhaps she was starting to get used to it.

They made it all the way to the coast.  To keep them as close as possible to the next day's destination, they had to land south from the closest major city, which meant that this night they would be camping.  They landed, and the dragon flew off to forage for the night's dinner, as the dragoneer and Christina prepared set up camp and prepared dinner for themselves from their packed supplies.

``I am surprised that you can trust it to return to us,''  Christina remarked to the dragoneer.  This was actually the first time that Christina had a chance to actually talk to the dragoneer;  in the air it was too noisy for more than the occasionally shouted update on their current progress, and the previous night she had been too famished and exhausted to have more than a token conversation with him.

``First of all, the dragon is not an `it';  his name is Arthur,'' the dragoneer replied.  ``Second, of course he will return!  If he doesn't take us to our destination, then he won't get paid.''

Christina was surprised by this information.  ``It... he... get's paid?''

``Of course he gets paid!  Do you think he would do this for free?''

Christina was not sure how to respond to this, so she replied, ``Well, umm, I didn't...''

The dragoneer shook his head.  ``I bet you though that Arthur was a pack animal, didn't you?''   He snorted.  ``Hmph!  Heroes -- so educated, and yet so ignorant.  So few people have interactions with dragons that they are often misunderstood, and rather than combatting this the Order actually encourages it by training its heros to think of dragons as nothing more than  large, blood-thirsty beasts.  After all, it wouldn't be suit them for you heros to give any second thought to killing them, now would it?''  The dragoneer took another bite of his meal, and then continued,  ``So, to answer your unspoken question, yes, Arthur is every bit as intelligence as you and I.  In fact, he is probably more intelligent, given that he is doing this passenger duty in order to pay for tuition for his doctoral program.''

``If dragons are so intelligent and scholarly, then why do they have an odd tendacy to end up as blood-thirsty guardians of the fortress of evil villains!''

The dragoneer shrugged.  ``Dragons are like people;  they aren't all alike.''

Christina pondered this for a moment, and then asked, ``What is Arthur studying?''

``Since you ask, he is going for his doctorate in Villain Studies,''  the dragoneer replied.  ``Part of the reason why he took this mission was because it would give him the chance to see an evil villain's lair close up -- though he is not stupid enough to actually want to \emph{land} on the island, since his soul would be in as much danger as yours.''  The pilot paused to take another bite.  ``Speaking of which, why on Earth are you going through with this mission, anyway?  It's not like we can do anything to actually hurt the Soul Eater.''

``Because doing something is better than nothing!'' Christina declared.

``Typical hero,'' the dragoneer replied, as he turned away to focus on his meal.

Christina wondered about what the pilot had told her.  She had killed a few dragons herself and hadn't had a second thought about it.  Were they really as intelligent as the pilot claimed?

As the sunlight died away, Arthur returned.  Christina saw him lift a sack from the cargo pouch.  He opened it, carefully remove a large book from it, and set it by the fire.  He then took out the largest pair of spectacles Christina had ever seen, put them on, and started read his book by the fire.

Well, I suppose that answers that question, she thought to herself.  ``Arthur?'' she asked him.  Arthur ignored her.  She whispered to the dragoneer, ``Can he talk?''

He snorted.  ``Of course he can talk!  Dragons could talk since before you and I were apes.  It's just that they tend to be very reticent, especially a scholarly bookwarm like Arthur.''

Christina tried a different approach.  If dragon academics were anything like human academics, they loved nothing more than to talk about what they knew.  So she asked, ``So, Arthur, what have you learned in your studies of villains?  Have you learned anything about the Soul Eater?''

This got Arthur's attention;  he placed his book on the ground and turned to look at her.  ``Many things I have learned,'' Arthur replied.  His voice was a very low bass, deep enough to for Christina to feel through her entire body, and at the same time so quiet that it was barely a whipser above the crackle of the fire.  ``What I have found to be most remarkable the variety of motivations that drive villains;  they are far more complicated than many people realize.  Many are motivated primarily by averice, and wear a mask of evil to intimidate rather than as a part of their identity.  At the other end of the spectrum, many do not care about riches at all, but simply delight in spreading suffering and misery.  The Incindor, for example, loves lighting villages on fire just to see them burn;  since this makes them difficult to pillage, however, he is among the poorest of villains.  Some, villains, such as Lord Voldemort, have a personal vendetta that they are pursuing, which is often not entirely unjustified.  Then there are those, such as the Soul Eater, who act purely in response to perceived provocation---''

``Hold on there!'' Christina interrupted.  ``The Soul Eater eats souls.  That is his nature;  provocation has nothing to do with it!''

``The Soul Eater has his own soul farm and cares little for riches.  What he hates, however, is having the sanctity of his home violated every hundred years, and every time it happens he terrorizes the land of the living in retaliation.''

``It is completely naive to think that if we stopped raiding his fortress, that he would just suddenly give up tormenting us!''

``How else can one explain the fact that the rate of his attacks has always jumped each time that the Order has raided his home, and then steadily dropped afterward until they are practically non-existent?  Believe me, the Soul Eater has been studied very thoroughly -- at least, as much as possible given the paucity of the data -- and this is the conclusion that has been reached by the experts.  But anyway, I have my studies to attend to.''  He picked up his book.

``Then you are a hypocrit!'' Christina exclaimed.  ``If you really believe that it is raiding his fortress that causes him to terrorize us, then why did you agree to take me there?''

``For three reasons,'' Arthur replied.  ``First and most importantly, the Soul Eater has always fascinated me and I am incredibly fortunate to have been given an opportunity to actually get paid while getting the chance to see his island fortress with my own eyes!  Second, the pay for this mission is very, very good given the hazard.  And thirdly, it will not be a \emph{dragon} that raises his ire, so \emph{we} will not be the ones who feel his wrath.  Why not profit from your foolishness?''  Christina then learned that it was possible for a dragon to smirk, as Arthur returned to his book.

Christina snorted to herself.  Academics -- always inevitable so naive when it comes to the dangers of the world!  As if the Soul Eater would suddenly stop picking on mankind after hundreds of years or terror just because we chose not to harass him back once a century.  What gave these academics the right to think such a silly thing, based on what they themselves admit are a `paucity of data'!  And to believe that some people call the Order is a waste of money.

On the other hand, it was a little disturbing that even the encyclopedia that the Order provided for its heroes (to prepare for the inevitable challenges of wit) failed to mention that dragons were intelligent, thoughtful beings.  She was fortunate that this had never come up on a mission before in her years as a hero, but it was still disturbing.  She would have to bring it up with Bill when she got back.

Ah well, tomorrow was promising to be a long day, so she had best get some rest.

\timeskip

%@-node:gcross.20081101130025.7:Flying; conversation with a dragon
%@+node:gcross.20081101130025.9:Christina descends to the island
The next morning they woke up, ate breakfast, and then Christina started getting her stuff together for the mission.  Just as she finished, the pilot told her, ``It's best that we leave now, so that we can catch the fortress just at the beginning of its window.''  They mounted Arthur, and took off into the sea.

It didn't take too long for the shore to completely vanish from sight.  As far as she could see, there was water in all directions.  Christina marveled at what it must have took for her predecessor to have found the fortress a hundred years ago, before they had navigational stones that told you where to go and how close you were to reach your destination.

Eventually Christina felt Arthur slow and start to lazily make circles in the sky.  Now that the rushing of wind was not so loud, the pilot was able to speak to Christina.  He turned to her and said, ``This is the spot.  We seem to be here a few minutes early;  it shouldn't be too long until -- oops, there it is!''

Christina, the pilot, and Arthur all looked down at the bright green light that was eminating from the ocean.  Arthur immediately turned and flew away from it just in time as a spray of water shot into the sky and nearly hit them.  Thunder roared as large waves shot out from the center in concentric circles.

Below them, a mountain stood protruding from the water.

As the thunder died down, the pilot turned and shouted to Christina,  ``Are you ready?''

``NO!  Hold on,'' she said, scrummaging through her bags.

She took out her sunglasses, put them on, and gave the pilot a thumbs-up.  ``It's showtime!'' she shouted as she grabbed the ropes of her `fall-breaker' and leapt off the dragon.

Her descent was slow enough that it was going to take her a couple of minutes to make it to her landing spot, so she filled the time by joyfully flying in circles around the island.  She should see if she could borrow do this again for fun sometime, she thought to herself.

Finally, she made the approach for her final landing.  She painted a mental bull-eye on a spot of the new island that was a bit darker than the rest, indicating the presence of a cave.  With precision, she maneuvered her way down and landed right in front of it;  she smoothly absorbed her weight into her legs so that she was able to stay standing.  She smiled with pride at the perfect landing as the fall-breaker fell on top of her and buried her.  She laughed as she emerged from under it.  Well, it looked like she'd already had her glitch of the mission!  That means that it should be smooth sailing from here.  At least, one could hope.

She entered the cave.
%@-node:gcross.20081101130025.9:Christina descends to the island
%@+node:gcross.20081106211237.2:Moat crossing and battle
After a short distance through the cave, she entered the hollow cavern within the mountain.  In the middle was a fortress whose walls were made up of green flames, which flickered with an unearthly slowness.  Surrounding this fortress was a moat filled with lava.

And crocadiles.

To make sure of the latter, Christina took a small piece of meat from her pack, and threw it into the moat.  A mouth snapped from the water and snatched the meat.  It kept its glowing eyes above the water, staring hungrily at her.

Christina chuckled through herself.  If the moat had only been filled with lava, then this would have been a lot harder.  She did a quick calculation in her head, took a deep breath, threw a larger piece of meat into the moat, and then jumped.

A mouth emerged to snatch up the meat, and closed just in time to feel Christina's feet landing on it.  By the time it started to shake her off she had already jumped off to land on another crocadile responding to the meat she had thrown during her first jump.  By this carefully choreographed dance she made her way across the lava on top of the mouths of crocadiles.

There was a reason she was a hero.

When she made it to the other side, she walked to a dark patch of the fortress which appeared to be the door.  Suddenly, a circle of green flames surrounded her from several feet away, and started to close in.

``Before you gain entrance, you must prove yourself to be the Master!'' a voice thundered.  Oddly, the voice was the exact same as that in the Puzzle Master, and every other fortress she had ever been in.  She remebered the first time she had heard it, it had really been quite imposing, but eventually one gets used to the theatrices.

But this was not a time for reflection.  The voice continued,  ``Turn the tumblers to match the five digit entrance code, and you shall be allowed in.  Match the wrong code, and your soul shall be consumed in fire!''

A set of five large tumblers with numbers appeared in front of her.  Christina walked forward and turned them to match the numbers: 1-2-3-4-5.

``Greetings, Master!'' the voice thundered as the flames dropped.  Christina laughed to herself.  One of these days, she supposed, villains would learn that there secret code was not nearly as clever as they thought it was.

The dark spot revealed itself to be a drawbridge which lowered itself across the moat of lava as Christina quickly jumped out of the way.

Just inside the fortress was a large group of shades, glowing figures which looked a lot like a human with a sheet over his head with two holes for eyes, and that just happened to be on fire.  Christina laughed at the rediculity of the image as they drew brightly flaming swords.

``We have been expecting you!'' they said in union.  Well, she had been told that the Soul Eater had not been expecting anybody to attack him, but Christina had learned by now that ``military intelligence'' was an oxymoron.  She casually drew her own glowing swords, drew a cloth from her pouch, and took a couple of moments to polish them as the army continued its collective speech, ``Give up now, foolish mortal, and we shall merely throw your body to the crocadiles to be consumed!''

If there was one thing that bad guys loved to do, it was talk.  She continued to polish her swords while they continued to speak,  ``If you choose to fight us, however, we will not rest with the destruction of your body.  We shall use our swords to peel your flesh off it like the skin of a beat, coat it with olive oil and pieces of peeled garlic, wrap it in oil, bake it in the oven until it is tender, cut it into slices and then feast upon it!''  (Author's Note:  This recipe works as well with beats as it does with souls!)

This speech was somehow both more and less graphic than ones she'd heard in the past.  She finished polishing her swords and put the cloth away.  ``Are you all done yet, or should I get out a book to read while you all keep going?''

They gave an unearthly cry as they rushed forward.

Christina felt that something was missing.  She grumbled to herself as she realized what it was:  her sunglasses had fallen off in the lava!  Ah well, she supposed she would simply have to defeat these bozos with a little less style.

She counted to herself as they rushed towards her.  1... 2... 3... 4...  She leapt to the side as the first row of them ran past into the lava and were snatched up by crocadiles.  She shook her head.  Sometimes it almost didn't seem fair.  But anyway, more time for that thought later.  The remainder of the crowd made a quick turn and suddenly she was surrounded.    The easy part was over.

Now it was time for the fun part!

She gave a Mel Gibson battle cry as she met their swords with her own.  One of the sheet-heads was a little slow.  She cut it in half, and the top half fell to the ground while the legs kept running towards her.  She dropped to the ground as swords flew over her head, picked up the running legs, and tossed them with force at her two sides, knocking one of the sheet-heads to the ground and another into the waiting mouth of a crocadile.

A shade dived at her.  She parried its blow with one hand and made a slash which cut its body vertically into two pieces which fell to the ground.  Since the shade was a little taller than her sword was long, she picked up the half with the arm that wasn't holding the sword and swung it around, knocking many of the shades to the ground.

She continued fighting in this manner until all of her opponents had been cut into pieces on the ground.

``Fool!  You really think that you have won?''  One disembodied head shouted.

``Yes,''  Christina answered, as she kicked the head into the lava and it disappeared with another gulp.  ``So, is anyone willing to surrender?''  she asked the rest of the pieces.

``Umm, I'd raise my hand, but I don't seem to have one any more,'' one answered.

``Too bad,'' Christina replied, as she picked it up and started to toss it into the lava.  The head screamed, and Christina dropped it to the ground.  She laughed.  ``Just messing with you!  Yeah, yeah, by the Code of the Order I hereby accept your surrender and will visit no more harm upon you.''

``Can I get in on that, too?''  another shade-fragment shouted.  ``And me!'' came the voice of another, as all of the pieces with mouths shouted and those with arms waived.

``Ditto for the rest of you too.  Anyway, I need to be going now,'' Christina replied.  She started to turn towards the entrence when a crocadile raised its head out of the lava and started to speak.  ``Thank you, kind sir -- oops, I mean miss!  The Master never bothers to feed us, so we only get to eat once every hundred years when a hero passes through.''  Christina thought for a moment, and then tossed the rest of her pack of raw meat into the lava.  It was immediately snatched up, and then one of the glowing eyes winked at her before sinking back below.

She started to walk into the doorway, and then froze as she heard an unearthly cry from somewhere within;  the Soul Eater was feeding.  She took a deep breath, straightened her resolve, and continued her way in.

\timeskip
%@nonl
%@-node:gcross.20081106211237.2:Moat crossing and battle
%@+node:gcross.20081106211237.3:A dinner interrupted
The Soul Eater took a bite from his plate.  Needs more garlic, he thought to himself.

Christina burst into the room, brandishing her two glowing swords.  ``Soul Eater, surrender yourself or prepare to meet the wrath of my swords!''  she proclaimed.

The Soul Eater groaned.  ``Why do you heros always have to interrupt my dinner?  You'd think that a demon could get a little peace in his own home...''

``YARGH!!!''  Christina screamed as she lunged towards him.

``Very well then, I surrender,'' the Soul Eater said, calmly.

``YA-- What?'' Christina said as she stopped herself short, causing her to trip over herself and stumble for a bit.  She collected herself and attempted to regain her composure while blushing.  ``Pardon me?'' she asked.

``I believe that by the Code of the Order, you are not allowed to hurt me after I surrender, correct?'' the Soul Eater replied.

``Well, technically,'' Christina grumbled.  ``But... the terms are that you must agree to surrender all of your treasure, or else I shall force you to pay!''

``Of course, of course.  Butler!''  he shouted.  A sheet-head entered the room.  ``Take this woman to the treasury and help her pack as much of it as she can take.''

``But,'' Christina fumed, ``you loathsome creature, I... you can't just surrender, we're supposed to fight!  Don't you care about your gold?''

The Soul Eater took another bite.  ``Oh, and Butler?  A little more garlic next time, if you please.  Ah, hero, no, why should I care?  What need have I for gold?  True, I used to enjoy watching the suffering that was caused by my stealing it, but I am growing old and don't have the energy for such adventures any more.  In fact, I was thinking of moving to a smaller place, so I appreciate you helping me clean this one out of its junk.''

Butler started to walk down the corridor, and gestured for Christina to follow.  ``This way, miss.''

Christina fumed, but started to turn to follow him.  She stopped an turned back, shaking her sword.  ``This won't be the last you'll see of me!'' she proclaimed, as she turned away and followed Butler.

``Of course,'' the Soul Eater said to himself, unheard, as he resumed his dinner.

\timeskip
%@-node:gcross.20081106211237.3:A dinner interrupted
%@+node:gcross.20081108185724.2:Raiding the treasury
Christina stared in awe.  She had never seen so much treasure in one place before.  Of course, it didn't help that she had never made it all the way to a villain's vault before, but she was sure that if she had it couldn't possibly have been as much as this.  She had to crane her head just to see the top of it.

A large number of shades were standing around.  ``We have been instructed to help you,'' one told her.  ``As you know, there is only a couple of hours left until this place leaves your world, and the master really wants all of this to have been loaded by then, so perhaps we should begin now?  Or do you need more time to gawk?''

Christina flushed.  ``No, no, here is my bag of holding.  Load it all in there,'' she said, handing the sheet-head a bag from her pouch.  She wondered how they could possibly load it all in time!

Answering her unspoken question, the shades flew into action, becoming blurs against the mountain of treasure.  A river of gold quickly flew down from the mountain and entered her bag.

After a fraction of a second, the bag had been filled and was dropped to the ground.  One of the shades looked at her.  ``You came all this way and went to all this trouble to take our master's treasure, and this was the biggest bag you could find?''

Christina stared for a moment.  This wasn't possible.  It was an infinite bag of holding, it wasn't possible to fill up.

She walked over and inspected it.  It did indeed appear to be full.  She lifted it;  it was heavy.  It wasn't supposed to be heavy.

Was it possible she brought the wrong bag?  No, of course not.  After all, she had already made that mistake once before, and to protect against doing it again she set up a system:  the infinite bag of holding was always kept in her top shelf, and all other bags were kept in other shelves.  Never one had she violated this, so it couldn't possibly be...

Then, suddenly, an image entered her mind of the night that Homer had helped her clean her place up... of Homer placing her decorated, decidedly non-infinite bag into her top shelf, and her not doing anything about it.

She groaned, and shook her head.

One of the shades grinned an unholy grin.  ``Wait... or perhaps you were supposed to have brought a larger bag?  Did you really just accidently bring the wrong bag all of this way?''  He started to chunkle.  ``I can't believe this.  I have seen heros do all many of stupid things before, but to make it all this way and have forgotten the means of taking your loot home...''  He broke into a laugh.

All of the rest of the shades followed.  Many of them collapsed against the walls, or on the ground, as they were overcome with laughter.

Christina's face grew redder and redder.  ``Stop laughing!'' she cried.  The shades ignored her.  ``STOP LAUGHING!'' she shouted louder.

``Not anyone!  Only a collosal \emph{fool}!''  one laughed.  He stopped for a moment, and looked at her closely.  ``Oh, wait a minute.  You are a human... female, aren't you?  Ah, now it makes sense;  we have heard the legends of the woman hero who never failed to snatch defeat from the jaws of victory, and I couldn't believe it.  But now that I've seen you in person... you are even \emph{stupider} than the stories had told!''  He started laughing again, louder than before.

``AAAAAA!'' Christina shouted, as she snapped.  She drew her two swords and started slashing the sheet-heads into pieces.

It took them a moment to realize what was happening, but by then it was too late.  ``Wait,'' one cried, ``we told you we surrendered!  We AUGH'' it shouted as it fell apart.

In a couple of minutes, it was all over;  body parts were strewn all over the floor.

Christina felt a little better, but... technically she had just performed a major violation of the Code.  You weren't supposed to attack people who surrendered without provocation, and she doubted that mocking would be considered sufficient cause.

Well, it's not like anybody would ever find out...

But the question remained:  what to do now?  She had a couple of hours to kill, and since everyone had surrendered and she had all of the treasure she could carry, there was nothing more that she could do.

Or was there...  She remembered the scream she heard as she entered the castle, and thought of the stories of the soul farm that was kept in this fortress.  But, she was only equipped to bring home treasure--or in theory she had been, at least--now equipped to rescue anyone... On the other hand, being a hero was all about being the queen of improvisation, was it not?  And it wasn't just about saving lives;  it was about saving souls!

She made her decision, and started to storm back upstairs as pieces of sheet-heads continued to groan behind her.

\timeskip
%@-node:gcross.20081108185724.2:Raiding the treasury
%@+node:gcross.20081108185724.3:Dessert interrupted
The Soul Eater took a whiff of the plate in front of him.  Delicious!  It had been forever since he had chocolate coated soul a la mode.  He started to take a bite;  thank Greg the Almighty that he dealt with the hero in time for desser--

``Soul Eater, I told you we would meet again!''  Christina shouted, swords drawn, as she stormed into the room and the Soul Eater, startled, dropped his fork.  He glared at her.  ``What do you want now?''

``Instruct your minions to free the souls in your farm!''

His eyes widened.  ``No, hero, you go too far!''

``Do you accept my terms, or shall we fight?'' she said, brandishing her weapons.

``Fool!''  he shouted  ``You don't know what this would mean to your world.  I was about to retire from raiding you entirely -- well, except perhaps for the occasional snack, of course -- but if you steal my food supply then I shall be forced to rob you of souls again!''

``Yeah, right, you expect me to believe that you were really about to stop raiding us?  That you would really be satisfied with your soul farm alone?'' she asked sarcastically.

``Haven't you noticed that my raids have been getting less and less frequent?''

``And I am suppose to believe that this is more than just a coincidence?''

``You don't understand,'' he sighed.   ``I... my stomach isn't like it used to be when I was younger.  I would prefer to eat the souls of your world but they are too... spicey.''

``Spicey?''  Christina asked.

``Yes... they have too much personality and character.  Part of the reason why I started a soul farm was to breed bland human beings who's souls sit much better with me.  I try spicing them up with garlic, but believe me it simply isn't the same...''

``Well, I don't care, you shall free them, or else!''

``Are you not listening to me?  I just told you that I am about to retire raiding your world \emph{unless} my soul farm is taken away from me and I have to start raiding again just to eat!  And I have put so, so many years into breeding them to be just right...  and now like the last hero you are going to force me to start all over again?  Didn't you learn from the last time your stupid order did this to me?''

Christina paused.  Really?  The last hero had freed souls from him?  Why hadn't she heard of this?  Was he speaking the truth?  Now that she thought about, it was true that he had been hearing of fewer raids of late... actually, it seems like he hasn't even raided every year of late.  And if she freed his souls, then he would indeed be motivated to raid more often.  But could she really be motivated to leave them behind?  That is a horrible possibility, but perhaps it would be in the interest of the greater good...

Then a picture entered her mind of a crowd cheering her triumphant return home, celebrating her rescue of innocent souls from the malevolent hands of the Soul Eater.  Could she really let them down?  Could she bring herself to return home empy-handed, yet again?

She was resolved:  the cheering crowds would be hers this time!

``Soul Eater, your word cannot distract me from the fact that you are holding innocent souls captive so that you can entreat upon them the greatest form of suffering known to humankind!''

``Can you really blame me?  A demon's got to eat...'' the Soul Eater grumbled.

``If you will not surrender them then prepare to feel my wrath!  YARRGH!'' she shouted, charging at him.

Suddenly, he transformed into a ball of fire.  ``Foolish hero!''  He shot bolts of flame towards her.

She dodged the first and deflected the second with her sword.

``Is that the best you can AIIEE'' she shouted as a shock wave threw her against the wall.  She looked around the room.  Projectiles... she needed projectiles...  She grabbed chairs and started tossing them at the ball of fire;  the were easily brushed aside, but as he was distracted she was able to get closer to him.  Now she was in sword-swinging range, but swords were not going to be the defeat of this demon, so she carefully swung her sword very slowly, holding onto it loosely, and acted surprised when the  Soul Eater blasted it out of her hand.  ``No!'' she shreaked.

``Expect no mercy from me, hero, for you shall receive--NO!'' it groaned as Christina Sceptre of Power was quickly yanked from her bag and with a click it shot to its full length into the Soul Eater.

Once again, Christina thought to herself, saved by a villain's need to monologue at the moment of perceived victory.

``Soul Eater, by the power of the Sceptre you will instruct your minions to assist me in freeing your captive souls.''

The ball of fire screeched, flickering, and finally settled down back into humanoid sheet-head form.  ``Very well, hero.  Butler!''  A shade entered the room.  ``Take us to the soul farm.''

``Wait, didn't I just kill...  Erm, I mean, how you can tell that this one is Butler?  Don't they all look alike?'' she asked the Soul Eater as they started their way down the corridor.

``Yes they do, hero, so I solved that problem by naming \emph{all} of my minions Butler in order to save myself trouble,'' the Soul Eater grumbled.

\timeskip
%@-node:gcross.20081108185724.3:Dessert interrupted
%@+node:gcross.20081108185724.4:Soul farm
Christina was disgusted.  Before her was a wall covered with hundreds of cages, with a naked human being in each one.  Excrement was piled in a pool underneath all of the cages.  The indecency of the whole thing horrified her!

What also amazed her, though, was how still they all were;  there was a blanket covering each head.

``How do you keep them all so sedate?''  she asked the Soul Eater.

``They are so stupid that when we cover their heads, they think it is night,'' he replied.

``Instruct your minions to free them!''  she commanded.

The Soul Eater grappled with himself for a moment, but as the stone of power inside of him flared he spat out the words, ``Release the humans!''

The sheet-heads in the room opened the cages.

``Wake up, you are free!'' she proclaimed to the humans inside.

They continued sleeping.

``Tell the minions to remove the blankets over their eyes,''  she commanded.

``Do as the hero requests,'' the soul eater spat, placing particular emphasis of disgust on the word `hero'.

``Are you sure you want to do this?  They are so stupid that the higher ones might just fall to their deaths.''

``Don't be ridiculous!  These are human beings, not animals.  Just do it.''

The minions went from cage to cage, pulling the blankets from the heads of the humans sleeping within.

``Wake up, sleepy-heads!  You are free!'' she shouted.  ``Oh, and get them some ladders while you are at it,'' she said to the Soul Eater.

As the blankets were removed, the humans started to roll around and wake up.  Some of them weren't looking where they were going and fell out of the cages.  The ones near the bottom just got bruised, but there were unpleasant cracks from the people falling from the higher ones.

Christina was dumbstruck.

``I told you so,'' said the Soul Eater, smugly.

``How... how do you normally get them down?'' Christina asked.

``With tongs,'' the Soul Eater replied.

``Then... order your minions to do whatever they need to do to get the humans down here unhurt,'' Christina ordered.

``You heard her, Butler.  Get the humans down here intact,'' the Soul Eater relayed to the sheet-heads.

They stopped unblinding the human and started making systematic use of tongs to lower the humans to the ground.  It is fortunate that they are so fast, she thought to herself, watching their blurred motions, given how many there are.

``How many people were disabled by the fall?''  Christina asked.

``In a way, you are fortunate.  Those were only necks that you heard breaking.  No humans were disabled;  some were merely killed is all.  So they will not be slowing you down, if that is what you were worried about,''  the Soul Eater replied, smirking.

Christina gasped;  it wasn't supposed to be happening this way.  What had happened to these people?

As if he hard hear her question, the Soul Eater continued, ``As I said;  I bred these humans to be as bland as possible so that their souls would go well with my stomach.  You should pay more attention to things, hero.''

``Well, bland or not they are still human, so wake them all up!''  Christina demanded.

``As you wish.''

The minions removed blankets from the heads of the remaining humans and soon all of them awoke.

``You are free!  Come with me, and I will take you all away from this place!''  Christina attempted to proclaim once more.

They ignored her, and ran around the room haphazardly, making random grunting noises.

``What part of they have been raised to be stupid didn't you understand, hero?  You pathetic humans actually need to be taught to talk, and it was not desirable for me to do so,'' the Soul Eater sneered.

Christina was stumped.  What was she supposed to do now?  These human beings were really no more than animals.

But they are more than animals, she thought to herself.  If they didn't have souls, after all, then they would have no value to the Soul Eater at all.

``How do you get them to move from place to place?'' Christina asked.

``We herd them, just like what you human beings call cattle,'' the Soul Eater replied.

``Then... herd them towards the exit.''

The Soul Eater nodded towards his minions, who started to herd the mass of wild humanity down the hallway to the entrance of the castle.

\timeskip

%@-node:gcross.20081108185724.4:Soul farm
%@+node:gcross.20081108185724.5:Crossing the moat, take 2
``Why can't you make them cross?''  Christina fumed.

``My minions are trying,'' the Soul Eater replied, ``but understandably, the humans are afraid of the lava, and they don't even know about the crocadiles.''

Christina watched as the mass of humans huddled around the start of the drawbridge, too afraid to cross but also afraid of the whips that were keeping them from retreating.

``Must we use whips?'' Christina asked.

``I would be happy to let them run amok again, if that is what you really want,'' the Soul Eater replied.

Christina sighed, then gasped.  As the throng of humans was pushed closer to the edge, some of them were getting perilously close to the edge.

Two eyes popped up from the lava.

Christina spoke quickly, ``Order the crocadiles not to eat the humans!''

The Soul Eater laughed, ``The crocadiles do not listen to me, nor do they need to be useful to me;  the only follow their own hunger.''

``Then, tell your minions to back off!''

``Too late,'' the Soul Eater replied smugly, as one of the humans was pushed off the edge by the people behind him.  Christina closed her eyes, waiting to hear the inevitable snap, or perhaps just a scream as flesh hit hot lava.

To her surprise, several moments later she realized that she had heard neither.  She opened her eyes again.  The human being was now actually being carried across the lava by a crocadile!

More people were being pushed into the lava, and more crocadiles arrived just in time to bear them across.

One poked its head out of the lava, winked at Christina, and said, ``We figured we owe you one, hero,'' and then took its turn in bearing a human across.

The Soul Eater shrieked.  ``Traitors!  Useless reptiles!  Don't you know who your Master is?'' he yelled.  Then he paused, thought for a moment, and then said more quietly,  ``Oh, that reminds me, I really should feed you one of these days, shouldn't I...''

During all of this, the humans, seeing that their members were crossing the lava unhurt, decided that the drawbridge wasn't so scary after all, so the mass decided to cross.  Some continued to fall off the sides, and were carried over by crocadiles as well.

Christina breathed a sigh of relief, and made her way following the humans down the cave, with the Soul Eater continuing in tow, tethered by the Sceptre of Power.

\timeskip
%@-node:gcross.20081108185724.5:Crossing the moat, take 2
%@+node:gcross.20081108185724.6:Departing the island
Well, the easy part is now over, Christina thought to herself, as she stared at the vast waters between her and the mainland.

``So, hero, what are you going to do now.''

She looked up, and saw a dragon circling overhead.  Something was headed... she jumped out of the way as an arrow struck the shore next to her.  There was a piece of paper rolled around the arrow.  She removed it and started to read.

\texttt{Hero, you are crazy if you think that we can bring all of these people home!  Even if Arthur were willing to fly that close, there is no way that he could possibly lift so many human beings at once.  So inflate the balloon and get up here already so that we can go home!}

Christina sighed.  Civilians could be so cowardly at times.  But he was right;  there was no way that Arthur could lift all of these people.  How on Earth was she going to get them home.

She thought about it for a few moments.  She needed some kind of craft that could carry them.  She didn't have anything that floated, however...

But she did have something that flew!  She could use her balloon to lift them into the sky, and then have Arthur pull them along!  But how was she going to get all of them attached to the balloon.  She could tie them, but she didn't have enough rope.

The ground started to shake, and there were many screams of panic from the former prisoners.  Then it settled again, but some of the water around it was starting to steam.

``Soul Eater, how much time do I have before this island leaves our world?''  Christina asked.

``About twenty minutes, hero,'' the Soul Eater replied.

Oh Greg, what do I do now?  she thought to herself.  What would Patrick have done in this situation.  Then it hit her:  he would fight for the good, not for the perfect.  If not everone could come with her, then not everyone was going to.

This changed the scale of the problem, but not its nature.  The humans continued to scramble around haphazardly.  It would be good if she could get them to calm down.  How was it that the Soul Eater had done it again?  That's right, blankets over their eyes.  If only she had...

Then it hit her.  She looked at her fallen fall-breaker.  It looked like it could hold about twenty people.  She turned to the Soul Eater and ordered, ``Instruct your minions to drive twenty of them under the cloth on the ground.''

``Under?''

``Yes, have some of them pick it up, and then drop it on their heads.''

They did so;  the humans underneath fell to the ground and started sleeping.

``Now tell them to wrap the humans up inside the cloth in a bundle.''

As they did this, the Soul Eater said to her, ``If you are only planning to take twenty people from me, then perhaps I shall only raid your world lightly in return.''

``Oh, I may only be able to take twenty people home from me, but I plan on saving \emph{all} of them.  Tell your minions to drive them into the sea.''

The Soul Eater snorted in fury.  ``What?  You will completely waste them?''

``I might not be able to save their bodies, but I can save their souls.''

``No, I refuse!  I...''  He fought the stone for a moment.

``Soul Eater, drive the humans into the sea!''  Christina ordered.

The Soul Eater slumped.  ``Minions, do as she commands,'' he commanded softly.

Christina watched as the frightened humans were forced to the shore, and then driven onward and onward, until they were all submerged.

For the first time in the last hour, it was perfectly quiet.  Christina couldn't help shedding a tear as she got the float ball out of her pocket, tied together some ropes to form a harness for herself, and then tied the end of the rope to the bundle of bodies in her fall-breaker.

Steam was now rising water just outside the shore.  She turned toward the Soul Eater and gave him one last order, ``You will return into your fortress and allow us to return unharmed.''

``As you command, hero.  But this time, let me be the one to say:  this will not be the last time that you see me,'' he growled, as Christina released him from the stone and he and his minions made their way back through the cave.

Christina squeezed the ball three times, and it inflated bringing her and her burden into the air.

\timeskip

%@-node:gcross.20081108185724.6:Departing the island
%@+node:gcross.20081108185724.8:Ascent
Christina was far above the island when it finally disappeared.  It's disappearance was not quite as dramatic as its arrival -- which was good thing, considering that she was not nearly as manueverable as Arthur had been! -- but it was still impressive.  It grew simultaneously brighter as the rock started to glow and darker as it sunk below the waters until the last of it had disappeared below the waters with a sudden flash.

She was worried for a moment that it might keep rising forever, but fortunately it eventually stopped rising just as Arthur arrived next to it.  The pilot shrugged at her.  They were too far apart to be able to hear each other, so Christina finished tying some of her rope into a hoop and tossed it just behind Arthur's neck;  he reflexively tried to dodge it, but instead managed to move his head right to where it was falling.  Christina smiled;  she was good.

Arthur turned towards her, and her body vibrated as she heard the words thunder out of his mouth, ``My fees have just doubled.''

He turned, and started flying back to the mainland, with Christina's balloon and cargo in tow.

%@-node:gcross.20081108185724.8:Ascent
%@+node:gmc.20081111201553.2:Triumphant arrival
After a couple of hours of flying, they finally arrived at the town of Wayton, a port city on the coast.  Christina looked down, and there was a crowd so large that it could clearly be seen from their height in the air.  Her heart was warmed;  there were there for her!

She looked up again and saw the dragoneer trying to tell her something.  He was still a little too far away to be heard, so after a few minutes Arthur turned his head to her and said sardonically,  ``Shall I assume, hero, that you have an equally brilliant plan for getting yourself down?''

Christina grinned.  Of course she did!  She pulled out her sword and cut herself free of Arthur.  Then she pulled herself up a little bit on the rope, and very carefully poked a small hole into the float ball.  There was a barely audible whistle as air flew out of the hole, and the ball began to lower itself to the ground.

As it did so, Christina realized that she was getting propelled away from the crowd, so she carefully punched another hole on the other side.

This made her fall a little faster.  After a few minutes, she saw more clearly that there was a stage set up for her, and she was slowly drifting away from it.  She carefully punched yet another hole in the ball, though a smaller one.  The ball started falling noticebly faster, though not alarmingly so.  She realized that she should be more sparing in the holes she used to manuever.

She continued to make her way slowly down, very occasionally punching another small hole in the float ball, until she was nearly at the ground.  By this time, her freed prisoners were nearly to the ground, just to the side of the platform; her aiming had been perfect.  Just as they touched the ground (with enough force to bruise, but hopefully not enough to break any bones) she cut a larger hole in the float ball to propell herself towards the stage.  When she was a few feet above, she dramatically leapt off and landed on her feet.  She bowed as the crowd started to cheer loudly, and the float ball collapsed on top of her.

Well, you can't have everything.

Since the float ball was wrecked by this point anyway, she cut herself free of it, took another bow, and walked over to the podium.  It had only taken her a few minutes to figure out her plan for getting down, so she had the rest of the trip to think about exactly what she was going to say.

She began, ``Thank you all for coming here today!  I am sorry to say that the Soul Eater is not quite as happy today as we are.''  Laughter.  ``For the first time, the Soul Eater has been forced to relinquish his ill-gotten treasure to us!''  Cheers.  Christina waited for the crowd to settle.  ``And the treasure I have recovered is far, far more valuable than silver or gold.  Many of you may have heard the stories of the Soul Farm that he kept to satisfy his unholy hunger.  Well, I can tell you that such a thing used to exist.. until today!  All of the souls in  his captivity have now been freed!''  Cheers.  She continued, ``The Soul Eater is going to be very hungry tonight, but please try not to weep too many tears from him.''  Laughter.  ``And so I present to you now:  the rescued souls!''  She ran off the platform and cut open the fall-breaker to reveal the pile of naked bodies within.

The crowds first reaction was to be shocked to see so much humanity presented so indecently, and wondering if they were even alive.  But as the former prisoners started to get up, the crowd started to cheer -- although there was still a touch of confusion in it revealed by the fact that they were not quite cheering as loudly as before.

The combination of seeing such a large group of people and hearing the roar of their cheers frightened the prisoners and caused them to huddle together.

But if the cheer was not as loud as before, or the prisoners no quite acting like they were happy to be free, Christina didn't notice.  This was her moment of triumph, and it was going to be viewed through rose-colored glasses no matter what actually happened.

She ran back up to the podium triumphantly, and continued to speak.  ``Now, these people were in very harsh conditions and will need your help.  I will be flying out tomorrow so I shall leave them in your care.  I beseige you to treat them as the long lost family members that they are and to ttreat them with kindness until they have recovered from the madness of their condition.  I promise you that the Order will recomponse you for your service in this.''  In her triumphant moved, she glossed over the fact that she would have to talk them into doing this;  but she was bouyed with confidence at this point and was convinced she could accomplish anything.

Meanwhile, as she was making this speech, one of the former prisoners got bold and walked up to a member of the crowd with a particularly colorful skirt.  Out of curiosity, he tugged on it, causing the woman to shriek and the man to respond in kind and to retreat back to his fellow prisoners.

Not noticing this, Christina continued, ``For too many years, the Soul Eater has made us all fearful of losing our souls.  We might not be able to hurt him physically, but that doesn't mean we can't make him hurt!  Today, for once \emph{we} have been the stealer of souls, and the Soul Eater has been the victim!''

Regardless of the oddity of the prisoners, this was definitely a fact worth cheering, and the crowd did not fail to disappoint.  Some of them started a chant, ``Chris-ti-na!  Chris-ti-na!'' and started moving closer to the podium.

Christina closed her eyes and savored the moment.  Then a thought occured to her, ``Oh!  They are moving closer to the podium!  That must mean that they want to carry me;  I have always wanted to be carried by a crowd!''  As they got closer, she grinner and jumped into them.

The people gasped in surprise and jumped out of her way as she hit the ground.  ``Ouch,'' she said to herself, rubbing her behind.  Ah well, things didn't have to be perfect this time, since she was sure that there would be a next time!

And while she had embarassed herself anyway, she took the opportunity to ask, ``By the way, would you all excuse me for a minute?  It's been a long day, and I really need to pee!''
`
\timeskip
%@-node:gmc.20081111201553.2:Triumphant arrival
%@+node:gcross.20081111232036.4:Celebration
To Christina's surprise, it proved difficult to get anyone to volunteer to take care of the prisoners.  Fortunately, there was a Gregorian Monestary in the town, and the monks agreed to take the people in and take care of them.  Although Christina was personally an athiest -- afterall, who could seriously believe in the existence of a omnibenevolent Author when creatures such as the Soul Eater were allowed to feed on peoples' souls? -- she had to admit that she was glad that other did and that it inspired them to do the dirty work for others.

After that was taken care of, it was time to get serious about celebrating!  The mayor of the town personally invited her to a dinner in a large hall which was packed with people who were thrilled to be around her.  After the dinner, there was dancing.  It was the happiest day of Christina's life, and she didn't want it to ever end.  However, she was only human, and eventually all of her trials of the day caught up with her and she left to go to bed.

A perfect day, she thought to herself as her head hit the pillow.  She was out in moments.

\timeskip
%@nonl
%@-node:gcross.20081111232036.4:Celebration
%@+node:gcross.20081111232036.7:Battle
She woke up to the sound of an unearthly scream which shook her to the core.  Lots more yelling could be heard by people outside.

She wasn't quite sure what was happening now, but as a hero her duty was to protect the people, so whatever was going on was her problem by definition.  She leapt out of bed, quickly dressed herself for battle, and then ran outside to see what was happening.

She ran outside and saw glowing shapes flying through the air.  Damn, she cursed to herself.  Shades from the Soul Eater, here on a raid.  She ran back into her room, tossed her metal swords to the ground, drew two glowing aether swords and charged back out.

The raid had just started, so people were still in the process of getting woken up.  Sheet-heads were moving into and out of buildings, causing screamings to be heard from the occupants who were often seen moments later running outside.

Many of the town policemen had started to be awaken at this point and were trying valiantly to fight the shades off.  However, their blades merely passed through the shades and so the shades either ignored them or struck them down.

They are playing with us, Christina thought to herself.

She ran up to one group of officers and started slashing her way through the sheets that were there.  Caught off guard, they easily fell to her aether swords.  ``Where is the captain?'' she barked.

One of them stepped forward and saluted,  ``I am, hero Christina.''

Christina shouted in anger,  ``Why in the name of Greg are you and your men attempting to fight these sheet-he-- I mean, shades with ordinary metal?  You should know perfectly well that this won't work!  Where are your aether-charged swords?''

``We... don't have any, hero.''

``\emph{What?}''

``Our budget was cut, and we had been so long without a raid and had heard that the Soul Eater was starting to retire anyway, and it is so incredibly expensive to re-charge the swords...'' the Captain replied, trembling.

Christina fumed.  Typical civilians, always coming up with silly reasons to believe that they don't need to spend time and money being prepared in case a villain raids!

Then she took a deep breath.  Be that as it may, it was what it was.

``Listen, Captain, I appreciate your spirit but you and your men are wasting your strength and bearing your souls to unnecessary risk.  Instead of fighting, have all of your men start evacuating the town;  get as many people as you can on horses and dragons, since they move too quickly for the shades to keep up with them!  Meanwhile, I will cover for you.''

``But... respectfully Christina, you may be a hero, but you are only one women...''

Christina held up her sword dramatically. ``That may be true, but--'' Christina started to say, but then quickly interrupted herself as she thrust her sword behind her in a slashing motion.  She turned around and stared with contempt at the glowing pieces on the ground.  ``Oh come on now you pathetic wretch;  if you are going to sneak up one someone then at least be sneaky about it!''  She turned back to the policemen.  ``I can take care of myself.  You all have neither the weapons or the training to fight this battle, and I have both.  Now go!  We have no time to waste.''

The Captain soluted again, and then ran off with his men, banging on doors and shouting for people to wake up.

Christina heard a shriek in a house close to her.  She ran over to it, kicked down the door, and watched as a sheet-head carefully made a scooping motion towards a man's head.  Christina didn't hesitate, but immediately throwed one of her swords, cutting off the shade's hand.  She ran over to him, making a quick slashing motion to her right on the way to disfigure the shade that was there, and the first shade shrieked and ran through the wall back out of the house.

``Quickly, run to the dragonyards, there is an evacuation there!'' she shouted as she ran back out the door.  

She heard a loud, thundering laugh inside the tavern next door, so she kicked down the door and ran inside.

There was a green fire in the fireplace.  The Soul Eater sat in one of the chair in front of it.  ``Ah, hero!  I told you we would meet again,'' he declared.  ``I bet that you never believed that it would be so soon!''

Christina fumed and ran towards him.  He allowed himself to pass down through the chair and then dodged out of her way as her own swords passed through it, missing him completely.  He resumed laughing, and said,  ``Really, hero, is that the best you can do?''  She threw a sword at him, and he responded by allowing himself to sink through the floor as the sword bounced off the wall.  She ran over to where he had been standing and thrust her sword into the floor.  She heard a horrible scream.

``Yes!'' she cheered to herself.

``Just kidding,'' a voice behind her said.  She instinctively responded by first slashing behind her and then turning around to see what was there.

The Soul Eater was standing in the doorway.  ``As the next few days pass, hero, I want you to remember one thing:  you did all of this to yourself.''

He then disappeared as one of her swords flew through the doorway, his grin being the last part of him to fade away.

She ran back outside and retrieved her sword.  No time to wonder what he meant, Christina throught to herself.  For now there are people to rescue!

She saw many of the shades starting to head towards the stables and the dragonyard.  Dammit, she couldn't be in too places at once!  Which of the two escape points should she be guarding?  She pondered this for a moment when she heard a voice next to her.  She turned to face it.

The man was tall, dark, and handsome, with a very muscular build.  Her mind faded away for a moment, and then she realized that he was talking to her.  ``Need any help?''  he asked.

She started to send him away, and then recognized a pin bearing symbol of the Order on his collar.  ``Oh, thank Greg!  Do you have any weapons of aether?''

``I don't,'' he replied, smiling.  ``But unless I am mistaken, you have two.''

``Oh,'' Christina said, blushing.  ``I suppose that I do.  Umm, here's one,'' she said, handing the sword to him.

``So, you defend the dragonyards and I'll defend the stables?''

``Wha--oh, right, of course!  Yes, let's do that!''  She ran off to the dragonyards.

\timeskip
%@-node:gcross.20081111232036.7:Battle
%@+node:gcross.20081113231052.2:Dragonyards
The scene was chaos.  People were trying to run around to avoid the soul-scooping shades while simultaneously loading themselves onto the dragons.  A few had already taken into the air.

She started to rush into the scene when she crashed into her dragoneer.

``Oh, thank Greg, hero, we have been waiting for you!''

She fumed.  ``Why on earth were you doing a silly thing like that?  Grab as many people as you can and get the heck out of here?''

``But hero, what about you?''

``I -- hold that thought,'' she answered as she slashed behind her.  She turned around;  there was nobody standing there.  Flushing she turned back to the dragoneer.  ``Nevermind that, just getting practice.  Anyway!  Don't worry about me, I can take care of myself.  Just go!''

``Uhh... right, okay then,'' the dragoneer replied, turning away from her and returning to Arthur.  He shook his head and muttered under his breath, ``Crazy heros!''

Now that she was still anyway, she paused for a moment to observe the scene.  The one thing working in their favor was that it took time and exertion for a shade to scoop out a soul, and since nobody was stupid enough to stand still for that long they had to restrain people long enough to do the deed.  Since there were so many people in one spot, the most that they could do is hurt and harass people and hope that they could knock someone down and isolate them long enough to steal the soul, which is what they were trying to do.  All she had to do was to keep them moving.

She raised her sword and shouted, ``All right sheet-heads, there is only one of me here so you will have to wait patiently for me to get around to cutting you into pieces.''

A couple of shades who had just knocked someone to the ground looked up at her in response to her declaration.  She winked at them, and they fled.

A few others had decided that there best bet was to pick up their prey and carry him away, but happily while carrying someone they moved too slowly and she was able to run up to them and chop of their arms.

While she was deciding on her next target, the dragon next to her was loading up and about to take off.  It turned to face her, and she then recognized that it was Arthur.  ``My fees have just \emph{tripled},'' he grumbled, and then took off into air.

By this point there were now very few dragons left on the ground.  On the bright side, this meant that they had fewer targets left, but the problem was that there were many more of them per target and unfortunately the number of heros hadn't increased.

She thought to her self, what would her favorite hero, Mel Gibson, do?  Doh!  Of course I know what he would do, she thought to herself.  She screamed a loud battle cry and rushed into battle with the biggest group of shades that she saw, who were harassing one of the few dragons on the ground.  They dispersed, but the members immediately joined groups harassing other dragons.  She ran at another group, and they dispersed again.  At least she was keeping them moving, but this was getting pretty ridiculous.

She heard a buzz behind her and reflexively swung her sword behind her;  it was stopped with a loud zap.  She turned around, and found herself pressing her sword against another.  She stared into his dark eyes for a moment.

He cleared his through.  ``Umm, I do believe that we are on the same side, are we not?''

``We are,'' she replied.

``Then... perhaps you could get off my sword?''  he asked calmly with a hint of humour in his voice.

``Oh!  Right,'' she replied as she withdrew her sword.  ``You got here just in time!  Let's go,'' she said, charging towards one group of sheet heads as the other hero charged towards another.  Between the two of them, they were able to keep the shades too busy worried about them to harass any more dragons, and pretty soon they were all in the air.

Only the Captain remained on the ground.  ``Why are you still here?'' Christina asked him while slicing a shade in two.

``There wasn't enough space for me on any of the dragons, and I felt that I deserved to remain behind after having been foolish enough to lapse in preparing for this.''

``I arrived here on a horse, policeman!  Quickly get on it and ride away,'' the other hero shouted as he spun in a circle and cut two shades that had been approaching him from both sides.

``No, you two leave;  this battle is not your responsibility, it is mine as the Captain of the police of Waytons.  Maybe you could let me borrow one of your swords, though?''

Christina fumed.  ``If you don't get on that horse right now and ride away then I will ensure that your soul is safe by personally cutting off your head!  We're heros;  we can take care of ourselves!'' she shouted, swing her sword behind her and again striking the other heros' sword.  ``You really need to learn to stop doing that,''  he quietly remarked to her.

``Uh, right,'' replied the Captain.  ``Thank you both, for everything.''  He hopped on the offered horse and rode off.

The shades they were fighting stopped and sank into the ground.

Then several new rows of shades rose up, this time bearing glowing swords of their own.

Christina and the hero were surrounded.  The pressed their backs against each other.  ``Try to only attack \emph{forward}, Christina,'' the other hero whispered.

Suprisingly, the shades did not attack right away, but instead waited.  They heard a booming laugh as the Soul Eater rose from the ground.  He kept laughing for a couple of minutes, and gave no indication that he was going to stop.

Christina relaxed and allowed her sword to fall to her side  She turned to face the other hero, who had done the same.  ``Why do villains laugh so much?  Nothing could possibly be that funny,'' the oher hero remarked.

``I don't know.  By-the-way, my name is Christina,'' Christina introduced herself as she offered her hand.

``Mark,'' replied Mark.

The Soul Eater continued to laugh.

``So, what are you doing here?  I didn't see you earlier today.''

He smiled.  ``You were having so much fun that I saw no need to dilute your festivaties with a second hero.  Was that your first crowd?''

``The first one I've earned, yes.  The first of many!''  she replied, grinning.  ``But anyway, what brought you to this town?''

The Soul Eater continued to laugh;  he was leaning against one of the sheet-heads for support now.

``Oh, the Order had reason to believe that the Shapeshifter was starting to operate in this area, so I was sent in to investigate.  As you can imagine, trying to figure out who might be is incredibly difficult;  I suppose that now that everyone has left there is not much point in remaining here.''

Christina groaned. ``Why is that villain still free?  We know he is going to relapse.  Damn liberals and their `Every villain sets a second chance!' policy.  Some days I really wish that... but no, so be it;  a stupid civilian government that occasionally makes bone-headed policies ain't perfect, but as Patrick Smith said we fight for the good and not for the perfect, so be it.''

``Indeed,'' Mark replied in agreement.

Now the Soul Eater was rolling on the ground in merriment.

Mark continued, ``You know, this laughing is starting to get on my nerve.  I wonder if there is anything we can do to stop it.''

``I know what to do, but you are going to hate me for it.  Okay, here it goes:  So there was this party, right?  A party of \emph{functions}!  And poor old $e^x$ was sitting along in a corner away from everyone else.  One of the functions walked up to him and asked, `So, why don't you integrate yourself?'  And $e^x$ replied, `I tried, but I already have!' ''

The Soul Eater stopped laughing.  He rolled over and looked at her.  ``That was not funny.''

``So what on Earth were you laughing at?  You have lost;  everyone in the town has been evacuated, and you know that there is no way you can win in battle against the two of us.''

``You are right, heros, everyone in the town has just been evacuated,'' the Soul Eater replied, returning to his feet.  ``And there is no way that my servants can stand against you, it is also true, which is why I didn't even bother wasting swords on them.  However, you will note that since everyone has left, you, Christina, are stuck here, and it will take you days to make it to the next town, which gives me plenty of time to carry out my \emph{true} plan.''

``Which is?''  she asked impatiently.

``You will find out soon enough.  Ouch!'' he said, rubbing his aethereal muscles.  ``I would laugh again, but the last laugh really drained me.  I really am getting to old to do this kind of thing anymore.  Ah well, it has been so long that I had almost forgotten how much fun being evil could be!  Farewell, heros.''

He and the rest of the shades started to sink into the ground.

Christina shook her sword at him,  ``This won't be the last that you see of us!''

``Indeed, I certainly hope that it won't be!'' the Soul Eater replied as his grinning head sank through the ground.

\timeskip

%@-node:gcross.20081113231052.2:Dragonyards
%@+node:gcross.20081115104035.5:Return to the inn
With the battle over and everyone in the town far away (and hopefully therefore safe), there was nothing to do but to head to bed.  It turned out that they were staying in the same place, the Red Dragon Inn, so they walked together back to the tavern, saying little as they each reflected on what had just happened.

Christina was filled with more loathing for the Soul Eater than ever before, but she was also torn.  Was all of this her fault?  Had she saved some, but only at the expense of others?  She had no idea how many souls had been lost tonight, but she did know that she had saved hundreds of souls the previous day, so hopefully it all worked out in her favor.

Mark was also deep in thought as he pondered his own dilemma.  I'm hungry, he thought to himself.  I wonder if the innkeeper would mind me stealing some of his food to make myself a snack;  I would like to think that I earned it!

Then the two of them had arrived, and Christina turned to return to her room as Mark turned to go to the kitchen.  She stopped, turned back to him, and said, ``Thank you, Mark.''

He smiled, and winked at her.  ``Any time.  We are both heros after all.  Heck, what would there be for us to do if there were no evil for us to fight?  Oh, and here is your sword,''  he said, starting to hand it to her.

Christina laughed.  ``It's not my sword, it's the Order's, so you might as well keep it just in case we need it again.  Though I really hope we don't,'' she continued, her smile vanishing.

Detecting her concern, Mark walked up to her and gave her a hug.  ``Don't worry, Christina.  I am sure this will all work out.  I don't know why the Soul Reader decided to raid this village, but it is such a rare thing for him to do nowadays that hopefully this won't become a regular occurange.''  He released her and grinned.  ``On a brighter note, who did you raid today, anyway?  I was so busy studying my notes that I didn't get a chance to ask anyone and find out!''

``I would rather not talk about that right now,'' Christina replied.

``Fair enough;  that was an exhausting battle so you can tell me the story another day.  Good night, Christina!''  he said, as he made his way back down the stairs.

He is so sweet, Christina thought to herself as she went to bed.

\timeskip
%@-node:gcross.20081115104035.5:Return to the inn
%@-node:gcross.20081108185724.9:Chapter 2: The Soul Eater
%@+node:gcross.20081108185724.12:Chapter 3: The Keeper of Maths
\chapter{The Keeper of Maths}

%@+node:gcross.20081115104035.6:The Journey, part 1
The next morning the both woke up and `borrowed' some of the innkeeper's food as they made themselves breakfast.  Well, `they' was a strong word;  Christina had the cooking skills of a karate blackbelt;  she could chop things in half, but that was it!  Fortunately, Mark turned out to be a very astute cook, and so she hung out with him in the kitchen as he made the two of them breakfast.  They chatted about trivial things, such as speculating on who the winner of the upcoming Quiddich Cup tournament would be.

They discussed their plans for the day, and decided that their best bet was to start making their way to the neighboring village and see if they could hire a horse there;  after all, after the scare they had last night it was difficult to see anyone returning for the next few days.

After breakfast, they packed up their stuff, and then started to make their way down the road to Whoville.

Christina was not in the mood to talk about herself, so she asked Mark about his various adventures and happily like all heros (except Christina, of course) he delighted in recounting stories of his triumps over incredible foes.  He was a very entertaining story-teller, though, so Christina enjoyed hearing his tales, and was so busy being entranced by his voice that she completely forgot to be jealous of his successes.

``Wait, so let me get this straight:  the Shapeshifter transformed himself to look like one of his guards, and yet you were able to defeat him anyway?  How on earth were you able to tell him apart?''  she asked.

``Simple.  I merely asked the guards which one of them was the real Shapeshifter, and he was the only one who didn't point to himself!''

She laughed.  ``I have never understood how villains are able to find troops who are so loyal to them;  it's not like they care at all about thier lives!''

``Too true,''  Mark replied.

``Or for that matter, it is absurd how so many of them think that we can be tricked or out-witted so easily!  I mean, when I stormed the Puzzle Master, he thought a mere crossword puzzle could stop me, as if he was the only one who could solve one of those!  Oh, wait, `Mark', now I remember hearing about you before!  You're the one that stormed the Keeper of Maths just a couple of months ago, right?''

``Uhh, yeah.''

``Ooo, I can't wait to hear the story behind that one!  What was the hardest math problem that you had to solve to get in?''

``Shoot, you know, I can't remember right now but it was this... umm... thing with some kind of trig function on top and an $x$ on the bottom and it went out to infinity, and...''

``$\int_0^{\infty}\!\frac{\sin x}{x}\,dx$?''

``Uh, yeah, that sounds right.''

``Dear lord, he could have at least asked you for a hard one!  I mean, who \emph{doesn't} know that the answer to that is $\frac{\pi}{2}$!''

``Umm, yeah, exactly.  Oh, and it is just so absurd that villains think that they always need to put crocadiles in their moats!  I mean, why not just open the drawbridge and let us in if you're going to make it so easy for us to cross.''

Christina laughed.  ``Yeah, really!  And they never feed the crocadiles anyway so it's not as if they are particularly loyal to them.''

They continued to talk and make fun of all of the various villains, and the absurd faults that they had which inevitably lead to their defeat over and over again by the heros of superior cunning.  Again, normally this was the kind of conversations that Christina shyed away from since it made her be too aware of her own faults, but she found that she enjoyed talking to Mark no matter what it was about.

As the sun started to set, they left the road and made camp in the woods.  Happily, it turned out that Mark was skilled in identifying mushrooms, and after a bit of searching he had been able to find a cache of delicious wild mushrooms which they spent the evening roasting over a fire.

At a break in the conversation, he asked her the inevitable question, ``So, who did you defeat yesterday?''

There was no hiding it.  ``The Soul Eater.''

``No, I mean before that.''

``That was before it.''

``Oh,'' Mark replied, and then became quiet for a moment.  ``That explains how he knew your name;  I had been curious about that.''  Another pause.  ``So, what happened?''

Christina proceeded to tell him the story, though with some... minor modifications.  She neglected to tell him about having brought the wrong bag, and instead made it sound as if she had been planing to free his souls all along.  She also neglected to tell him about how she had driven most of them into the sea.  After all, it wasn't as if there were anyway he could find out, and what he didn't know wouldn't hurt him.

After she finished telling him the story, he was quiet for a few minutes.  ``Hmm...  I wonder if the Order knew how he was going to respond to the raid on his fortress.''

``Well, it wouldn't be the first time that the Order knew something and didn't tell us!  Did you realize that dragons can talk?''

He raised his eyebrows.  ``What?  They can talk?''

``Yeah, I had a conversation with the dragon who brought me here, in fact.''

``Really?  Then why do we usually never hear them speak?''

``They're just very reticent creatures is all.''

Mark thought about this for a moment.  ``But... the Hero Manual clearly describes them as being dumb, blood-thirsty animals.  Very strange.  Well, I believe you;  after all, why would one hero lie to another?''

Christina forced a smile at the absurdity of the remark, but her heart sunk on the inside.

\timeskip

%@-node:gcross.20081115104035.6:The Journey, part 1
%@+node:gcross.20081115104035.7:The Journey, part 2
They continued their travels the next day, but in the afternoon clouds started to gather and since there was no hurry to get to Whoville they set up shelter and spent the evening huddled together underneath it -- a circumstance which Christina thoroughly enjoyed.  She hadn't felt this close to a man since she became friends with Homer.

The rains ended the next morning, and they continued to make their way to Whoville, growing increasingly companiable.

Finally, the following day they arrived into Whoville.

\timeskip


%@-node:gcross.20081115104035.7:The Journey, part 2
%@+node:gcross.20081115104035.8:Arrival 1
It was a cloudy day when the heros arrived in Whoville, and their reception there was about as warm as the temperature.  As they walked into the town, people looked their way, frowned, and then ignored them and returned immediately to what they were doing.  It was an unusually cool reception for a pair of heros.

``Very strange,'' Mark commented.  ``Is it just me, or are you getting a vibe that we aren't welcome here as well?''

``Yeah,'' Christina replied, a little nervous.  ``I was thinking the same thing.''

At one point a woman ran up to them and shouted,  ``Heros!  Why don't you bring the wrath of villains somewhere else?''

``Don't be naive!  Villains attack because they are villains, not because we raid them!''  Christina shouted defensively.

``Hmph, like we should listen to you!  You are the one that got us into this,'' the woman angrily replied.

``What are you talking about?'' Christina asked.

``Don't play ignorant, Christina, we know all about you, and you are not welcome here!''  She spat at their feet, and then ran off.

Mark turned to Christina, ``Is there something I should--''

``No, nothing, I don't know what they are talking about!''  Christina replied defensively.

``Okay,'' Mark replied.

They made their way to the local Enterprise Rent-a-Horse.  The man inside scoffed at them.  ``Good!  I see that you all are finding the most expedient possible way to leave this village.  We would be glad to take your money to help you with this''

``Why on earth are you so hostile to us?'' Mark asked.

``You mean, she didn't tell you?'' the man replied.  ``Here,'' he said, placing a piece of parchment on the table.  It was obviously magical, since...

``Oh, shit,'' Christina said, as she watched the images on it.

\begin{quote}
``Are you not listening to me?  I just told you that I am about to retire raiding your world \emph{unless} my soul farm is taken away from me and I have to start raiding again just to eat!  And I have put so, so many years into breeding them to be just right...  and now like the last hero you are going to force me to start all over again?  Didn't you learn from the last time your stupid order did this to me?''

``If you will not surrender them then prepare to feel my wrath!  YARRGH!''
\end{quote}

Hey, that's not fair!  He totally skipped over some parts, she thought to herself.

Oh, shoot.  The next part was worst.

\begin{quote}
``AAAAAA!''

``Wait, we told you we surrendered!  We AUGH''

In a couple of minutes, it was all over;  body parts were strewn all over the floor.
\end{quote}

Christina wanted to close her eyes, but she couldn't.

\begin{quote}
``Soul Eater, drive the humans into the sea!''

``Minions, do as she commands.''

The frightened, naked humans were forced to the shore, and then driven onward and onward, until they were all submerged.
\end{quote}

Shoot.

Now the Soul Eater appeared on the parchment.

\begin{quote}
``Ladies and gentlemen, I am getting old.  I would like nothing more than to retire and stop raiding your world.  I created a Soul Farm precisely so that I would no longer need to.  I warned your hero that if she freed the souls in my farm, I would be forced to raid again and again simply in order to eat.  But as you can see, she simply refused to listen to me.

``This should not be surprising given how reckless she is.  She slaughtered several of my minions even after they had surrendered, apparently just because she felt like it.  Some `hero'.

``Oh, and most of the people she rescued?  As you saw, she didn't even bother to save the vast majority of them because it would have been too inconvenient.  Instead, she used a Sceptre of Power and \emph{forced} me to drive them into the sea, keeping just a handful alive so that she could pretend to you all like she had accomplished some good.

``Ladies and gentlemen, I apologize for the fact that my raids are harming you.  Truly, I would like nothing more than to stop them.  But I simply cannot ignore the actions of your so-called `hero'.  Perhaps next time you all will reconsider who it is that you choose to protect you.''
\end{quote}

Then the scene started back from the beginning as the store manager rolled it back up and put it away.

``So follow me and let me lend you some horses already so you can get the heck out of here!''  the man grunted as he lead them to the stables.

Christina was nearly in tears, but heros don't cry so she swallowed them down

Mark was very quiet as well.  Fortunately, he had money on him so he was able to pay for the horses, and then they were off.

As they left the town, a crowd jeered them on, many of them bearing signs with vile sayings.

\timeskip
%@-node:gcross.20081115104035.8:Arrival 1
%@+node:gcross.20081115104035.9:Dark Secrets Revealed
They were quiet as they made their way down the road back to the capital, but unfortunately this time it was not so companionable.

Eventually, it started to grow dark and clouds started to fill the sky.  Mark said, ``So, Christina, I doubt that we are going to want to be staying in towns anyway until we get back, so we may as well go ahead and make camp.''

``I guess so,'' she whispered.

Once again they found themselves huddled under a shelter.  After an hour of sitting together in awkward silence, Mark turned to her and said,  ``Christina, I want you to tell me the story of what happened again.  But this time, don't leave anything out.''

A tear started to form on her eye, and this time she told him the full story, stupid mistakes and all.

Fortunately, Mark was a very sympathetic listener.  When she was finished, he replied, ``I can understand why you left some parts out before.''

Christina started to cry;  tears in public were one thing, but what was the point of being alone with another hero if you couldn't let yourself go?

``I... I am just such a failure as a hero.''

Mark shook his head.  ``Look... you may have made some mistakes, but... you know, all heros do.''

``Really?'' Christina replied.

``It's something we don't talk about.  It is understood that...  well, you see, when you win, people rarely question how it was done.''  He sighed.  ``You know, I was very hurt at first, but then I thought about how I have... edited, my own stories, for example.''

Christina waited for him to continue.

``I... there was a reason that I never got around to telling you the full story about how I defeated the Keeper of Maths.''

``Oh, that's right, the one where you had to compute $\int_0^{\infty}\!\frac{\sin x}{x}\,dx=\frac{\pi}{2}$,'' Christina interrupted.

``Yeah, that one.  So, the thing is, I actually didn't compute that integral myself.''

Christina face filled with confusion.  ``You didn't?  Then... how did you get in?''

``I had someone else do the integral for me.  I... So, as you know the Keeper of Maths has a daughter who is a mathematical prodigy, and...''

Christina was shocked, ``You didn't!''

Mark lowered his head.  ``Yes, I was actually on my way out of the fortress when I ran into her, and then I got the idea that if I couldn't do the integral, maybe she could so I... made her be too afraid to not help me solve it.''

Christina fumed, ``You know that by the Code the family of villains are off-limits!  Especially his daughter;  I couldn't imagine someone more innocent for you to pick on!''

``I... am not proud of what I did.''

``And if anyone outside had heard what you -- oh,'' Christina stopped in mid-sentance, realizing what she was saying.

``Exactly.  But since we are heros, after all, men and women of honor bound by the code, who on earth would believe a villain's word over our own?  And mine is not the only example, Christina.  Many heros have made similar mistakes.  It had just never occurred to anyone that our adventures might be recorded and presented by someone other than ourselves.  In fact, I think that after your example we are all going to have to watch our own decisions more closely.''

``So... the other heros will understand that I made a mistake?''

``Of course... but... well, we'll see what happens.''

Christina wasn't sure whether she felt better or not.  They could hear the rain pouring down very hard now outside their tent.  At some point Mark moved closer to her and started to hold her, and she pressed herself into him.

\timeskip
%@-node:gcross.20081115104035.9:Dark Secrets Revealed
%@+node:gcross.20081116140142.4:Arrival 2
It took them several more days to make their way back to the capital.  Occasionally they would come near a town, and Mark would leave Christina behind to purchase more supplies for the two of them.  Christina started to feel a little better, but she still had a heavy sense of dread over what would happen when they arrived at the capital.  There was a slight silver lining, though, which was that she and Mark were getting increasingly close after the time spent together, especially after having shared their dark secrets with each others.

Eventually, their journey came to an end, and they arrived at the capital -- just in time to see a massive protest with what looked like a thousand people marching on the Order's offices.  Many of them had rough sketches of Christina's face, overlayed by a red circle with a slash through it.  Others we're repeats of pacifists signs that Christina had seen before.

``Why am I always the one who gets the pacifists,'' Christina grumbled.

``We could continue camping outside the city to wait for them to disperse,'' Mark offered.

Christina shook her head.  ``No, there's no point.  Who know's how long they will stay here?  Besides, I am used to disappointing crowds;  it's no big deal.''  She took a breath.  ``Okay, c'mon, let's go.''

They made their way to the Enterprise rent-a-horse and dropped their horses off there.  Fortunately, people in the Capital were the most sympathetic to the Order that one could find, so they didn't receive any grief from the store manager there.

``Are you sure that you want to do this now?''  Mark asked.

``Yes;  may as well just get it over with.''

They started making their way through the crowd to the Offices.  As they did, people started to recognize Christina's face, and they started booing.  Christina was crying on the inside, but she kept her face made of iron.  Eventually, the made it all the way to the doors, and the guards there let them in.

Christina turned to Mark and said, ``I need to go see Bill.''

He nodded.  ``I need to report to Phil what I learned about the Shapeshifter.''

``So.''  She said.  Mark leaned over and kissed her on the cheek.  ``You'll be fine, Christina, no matter what happens.''

Tears nearly flowed down cheek again, but she managed to hold them off as she turned away and went to go see Bill.

\timeskip

%@-node:gcross.20081116140142.4:Arrival 2
%@+node:gcross.20081116140142.5:Final meeting with Bill
Bill sighed.  ``Christina... look...'' he started, and then shook his head.  ``The whole of Parliament is on our heads here, demanding to know why we provoked the Soul Eater into counter-attacking.  We told them the truth:  You had never been authorized to free the souls in the Soul Eater's Soul Farm.  ''

``I should have been!''

``No, you shouldn't have.  We... had suspicions that the Soul Eater was about to retire and wouldn't mind losing his treasure, but would mind losing his soul farm.  We just couldn't bring ourselves to tell you that you were not supposed to rescue anyone, not that it was clear that we would have been able to equip you to save so many people anyway on such short notice.''

``But... I was able to save their souls anyway!''

``That's true and... quite frankly, that was probably the best you could have done, it is true,'' he remarked, not unkindly.  ``But `logic' aside, the image of you driving all of those people into the sea looks absolutely horrible and hasn't helped your case one bit in the realm of politics!''

Christina was silent.

``Listen, Christina...  as much as I have beat on you on the past for your poor performance, you are one of us and no one wants to let you go, so we think that we have a solution.  Since you have at least been able to bring back a large amout of treasure from the Soul Eater, we will use that to justify keeping you on the payroll somehow and switch you to an administrative position, possibly as a trainer or a teacher.  We will portray it as the fact that since you have obviously demonstrated the ability to carry out at least one missions successfully, you have clear skills that make you worth keeping around, even if we no longer trust you enough to go on adventuring duty.  Does that seem reasonable to you?''

Christina hung her head.

``I know that it must sound incredibly disappointing to you, but...''

``No, Bill, that's not it...''

``Then what's...'' he stopped mid-sentance, and rested his forehead in his hand.  ``Oh, shoot...  what did you do this time?''

``I...  There was a mixup, and I brought the wrong bag of holding.  There is no treasure.''

Bill's face flushed with anger, and he raised his voice.  ``Greg damn it Christina, you make it hard as hell to fight for you, do you know that?  Do you have any idea how hard I have had to work to convince my higher-ups that you had potential and we just needed to give you more time to show yourself?''

At tear started to flow down Christina's cheek.

Bill took a deep breath and allowed the color to fade from his cheeks.  He continued more quietly,  ``Look... I'm sorry, there is nothing more that I can do for you.  You haven't completed a single mission we have assigned, and---''

``I defeated Lord Voldemort!''  Christina interjected defensively.

``That's true, you did, but recovering ten gold pieces from a 12-year old boy hardly counts.''  He took a deep breath, and continued.  ``Christina... I am going to go meet with my superiors now, and they are most likely going to agree to let you go, and to announce publicly that we have done this because you violated orders and brought danger on the land.''

``But you never told me not to save anyone!''  Christina cried.

``Indeed I didn't, and... look, I don't make it a point of questioning the decisions that my heros make on the ground.  If it were up to me, we would be doing just as I said:  transferring you to a different position.  But my superiors are feeling a great deal of political pressure and I doubt that I will be able to convince them not to make a scapegoat out of you.  It's ugly, but it's the truth.''  Bill sank back into his chair.  ``Look, Christina... the good news is that he hope that this will be enough to appease the crowd surrounding these offices so that they disperse and leave you alone for a while.  So why don't you stay here for a few hours, and go home after things have cleared up.  You will have a week to pack your bags.  And...  listen, you might not belong to the Order much longer, but I still consider you to be my responsibility, so... please come back to me before the end of that time, and I'll see what I can do about helping you find a job somewhere else.''

Christina just sat quietly as Bill stood up, gave her a pat on the back, and left her alone in the room.

 \timeskip

%@-node:gcross.20081116140142.5:Final meeting with Bill
%@+node:gcross.20081116140142.6:Bad times at the bar
Christina spent several hours sitting quitely in Bill's office until he returned.

``All right, Christina.  The crowd is now gone;  you should go home now.''

She picked herself up and headed out -- but not back to her place;  she was not in the mood for that just yet.  Instead she went to the Red Dragon Inn.

This time, happily, Homer was there.

He ran up to her and gave her a hug as he saw her enter.  ``I heard about what happened!  I'm so sorry.''

``Yeah... so am I.''

They walked to the bar and sat down there as Mark ordered her a drink.  ``How are you doing?''  he asked.

``You know... in a way, the worst of it is over.  For the last several days I've been under this cloud of dread, worrying about what was going to happen when I got back, and now I've experienced it.''

``Yeah, that must have made the ride home be horrible!''

Christina smiled and blushed a little, ``Oh, it wasn't all bad.  There was this really nice hero who I met fighting shades in Wayton, and he was very comforting.''

Homer smiled.  ``Very comforting, eh?  Tell me more about him.''

``Well... he's tall, dark, and handsome, and he is an amazing cook, and... I really felt like we were connecting on the ride back, like you and I do.''

``That's wonderful to hear!''

``Yeah, I know, thank God at least something seems to be going right.''  She took a swallow from her drink.  ``You know, I guess it could be worse;  I'm out of the order, but Bill at least said that he was going to try and find me employment elsewhere.''  She reflected for a moment.  ``You know, Bill might be a hard-ass at times, but he's a good guy.''

``The Order is generally pretty good about promoting good heros to be commanders, even if the higher-ups themselves are not so great,'' Homer remarked.

``Yeah, it's true.''

Homer punched her in the shoulder.  ``Well, I am incredibly happy to see that you are not feeling too bad, buddy, all things considered.''

Christina grinned.  ``Yeah;  heh, I really wonder what is in store for me next?''

She heard the door opening, and looked over in time to see a tall, dark, and handsome man enter the Red Dragon Inn.  She took a breath, and flushed.  It was Mark, and... he was looking at her... looking deep into her eyes.  She knew that there had been a connection between them, but this was the first time she had felt it so strongly.  She felt her heart racing.  She hated looking away, but she figured it was important to quickly check behind her to see if there were any girls there.  Nope, only Homer.  Mark really was looking her.

She melted as he walked towards her.

And then walked right past her up to Homer.

She watched the two of them looking deep into each others' eyes, obvlivious to the rest of the room.  ``I had heard that there was another hero who played on the other team,'' Mark whispered, ``but I had no idea that he was so handsome.''

Homer blushed, and the two of them embraces.  ``Let's take a walk,'' he said to Mark.  They joined arms and left the inn, still gazing each other and completely oblivious to the rest of the room.

Which, unfortunately, included Christina, whose jaw was on the floor.

``Augh!'' she cursed as she picked her jaw up from the ground and re-attached it to her head.  ``Greg damn it, I really need to get my jawbone looked at by a doctor sometime.  That really hurt!''  she remarked to herself, rubbing her jawbone.

She stared at the door, which had just closed behind the happy couple.  ``And yet... that somehow hurt a whole lot more.''

Some of the people in the Inn were staring at her.  ``Are you--'' one of them started to ask, and she drew her sword and glared.  ``No questions!''  The woman quickly turned away and forced a conversation with her friends.

Christina resheathed her sword and turned back to the bartender.  ``Another drink,'' she said.

``Umm, Christina, since you are no longer a member of the order we--'' he started to say, but then she drew her sword again and shouted ``Charge it to Homer!  He owes me.''

``Umm... of course he-- I mean, Christina.''

She resheather her sword and sank her head into her arms.

\timeskip
%@-node:gcross.20081116140142.6:Bad times at the bar
%@+node:gcross.20081116140142.7:A meeting
As Christina left the bar, she was simultaneously overflowing with spirits and completely empty of them.  She started to walk back to the barracks when she heard a voice behind her say, ``The Order is stupid to have cast off such a talented woman.''

She turned around, and saw a woman dressed in black with her hear bundled in a thick ponytail behind her head.  The woman continued, ``Fortunately, not everyone is so foolish.''

Christina rubbed her forehead with her hand, and replied, ``Ugh... if there is anyone out there who actually values me, I'd be very surprised.''

``Be surprised then, Christina.  I would like to hire you to help me with a job.''

Christina sharply dropped her and and looked up at the woman.  ``What?  You want to hire me? Who are you?''

``My name is Angela, and I am a privateer.  Like you, I happen to enjoy retrieving ill-gotten treasure from villains, but unlike you I personally did not feel that the blatantly sexist Order was the way to accomplish this.''

``They're not so bad...''

``You can really say that after the way they treated you today?''

Christina was having trouble thinking through her clouded brain, but she supposed that the woman probably had a point.  Something about this was bothering her, though...  ``Who is the target?'' she asked.

``The Keeper of Maths.''

Christina was startled.  ``The Keeper of Maths?  Ooo, I've wanted to go after him for the longest time;  that sounds like so much fun!  I have never had the chance to show off my excellent integrating skills, and--'' she stopped herself mid-sentence.  ``Wait, didn't he recently surrender and so is off-limits to us now?''

Angela laughed.  ``Technically, I suppose that attacking her would violate the Code of the Order.  Happily, though, neither you are I are in the Order, so there is no reason to consider ourselves to be bound by it.''

``But still... it's illegal...''

``Oh come on, you and I know that once a villain, always a villain;  it is only a matter of time before the evidence turns up to show that the Keeper was still being villainous, and everyone knows this.  So, yes, technically it's illegal, but I personally have found that people tend to look the other way.''

``I still don't know about this...''

Angela opened her arms.  ``Christina, don't you see?  You and I would make the perfect team!  You're only problem is that you sometimes forget important things, but thorough planning and follow-through is exactly what I am good at!  And I need someone who is not only an awesome fighter, but who has brilliant math skills, and you were the top of the class were you not?''

``Well,'' Christina could not help grinning, ``yes, in fact I was...''

``See?  The truth of the matter, Christina, is that I simply can't do this without you.  Are you in?''

Christina felt like she should not be making a decision like this at the spur of the moment, but this thought was completely overwhelmed by a deepered instinct:  someone actually wants me!  ``When do we leave?''  she asked.

``Right now,'' Angela replied.

``What?''

``Well, that is, after you finish packing.  I hired a coach that will leave as soon as we get to him.  It is a very comfortable coach, with a comfortable area for you to sleep in.''

``Why the rush?''

``Oh, don't get me wrong, the rush is not for me, it is for \emph{your} benefit, so you can complete the raid, get some serious money in your pocket, and return to your barracks in time to pick up your stuff and move out;  with the extra cash, finding a new place shouldn't be as hard.  As for why we are leaving tonight... well, quite frankly I doubt that you will be getting up early tomorrow morning, so I figured it was best just to leave now and let you sleep as long as you like.''

Wow, she really thought of everything.  ``Okay... I will go and pack right now.  Where should I meet you?''

``At the exit gate of the city.  See you soon,'' Angela said, turning to leave.

Christina headed back to the barracks.

\timeskip
%@-node:gcross.20081116140142.7:A meeting
%@+node:gcross.20081116140142.8:Resolve firming
As she walked down the hallway to her room, there was a little part of Christina which was still wondering if this was a good idea.  After all, Bill had offered to help her find a new job, so maybe she should stick around.

Then she passed Homer's room, and heard some things that she really had not wanted to hear.

That was enough to make her realize that she really had to leave this place far behind as soon as possible.

She packed up her stuff, including her single aether-charged sword -- just in case -- and headed to the city gate.

\timeskip
%@-node:gcross.20081116140142.8:Resolve firming
%@+node:gcross.20081116140142.9:Departure
There is no possible way that this could be my carriage, Christina thought to herself.  It was large enough to hold a couple of families, with both a deck that one could sit on to watch the scenery go by and also a closed-door chamber for privacy.

She saw Angela walk around from behind the carriage.  ``Ah, Christina, you packed a lot faster than I thought you would.''

``I was feeling motivated,'' Christina replied, darkly.

``I am glad to hear that!  Here, let me show you your room.''

``I have a room?  Inside a carriage?''

``Yep, with a bed and everything.''

Angela opened the door, and Christina was surprised to indeed see a narrow room with a small but very soft looking bed.  ``How on earth can you afford this,'' Christina asked.

``One of the perks of being a privateer is that you get to keep everything that you find.''

``Wow...'' As Christina gazed at the bed, she felt the weight of the day and of the alcohol catching up to her.  ``You know... would you mind if I just collapsed in that wonderful bed right now?''  she asked.

Angela smiled.  ``Of course!  That's what it's there for.  Feel free to sleep in as long as you like.  There is also water and some dried food in the cabinets underneath your bed, and the door in the back opens to a privy;  please remember to lock it since will both be sharing it.  When you start to feel a little better tomorrow, come up to the deck and we'll talk more.''

``Thank you,'' Christina replied with extreme gratitude.  She entered her private (!) room, set down her stuff, and was lying down for only seconds when she immediately fell asleep.

\timeskip
%@-node:gcross.20081116140142.9:Departure
%@+node:gcross.20081117194405.2:A silly dream
There was laughing.  Why did villains always laugh.

Christina looked around, then gasped.  These aren't villains laughing at her -- these are heros!

She was surounded by heroes, all of them laughing at her.

``Stop laughing!''  she shouted.

They didn't.

``STOP LAUGHING!''  she screamed.  She drew her sword.

They still didn't.

``AAAAA!!'' she screamed as she started chopping them apart.  In a couple of minutes, they were nothing but fragments on the ground, and yet were still laughing.  ``That is \emph{so} unfair,'' she grumbled to herself.

``At least you know now who your true enemies are,'' a voice remarked.

``What?'' Christina said as she turned around to face the voice.  It was the Soul Eater.  ``You are the true enemy here!''

``Am I?  I have something to tell you, Christina... \emph{I am your mother!}''

``Umm... what?''

``Join me, Christina, and we shall rule the world together as mother and daughter!''

The Soul Eater pulled back the robe on his head, revealing the face of Angela.

``What?  That doesn't even make sense,'' responded Christina.  ``Oh, wait, of course it doesn't make sense.  I'm dreaming, aren't I?''

``Took you long enough to figure it out.''

``\emph{Shut up!}  I was talking to myself, not to you.''

``Is there a difference?''  the woman asked, as her face morphed into Christina's.

``Umm...''  The dream started to fade.  ``Wait!'' Christina shouted.  ``I really don't feel like waking up just yet.''  The dream continued to fade.  Then Christina remembered a trick that she had heard.  She spun herself around until she felt the fading stop. ``Much better,'' she remarked.  ``Hmm, it's intersting how inside my dreams my internal monologue seems to keep externalizing itself...  Anyway.''  She turned to face herself and then sat down.  ``Please continue talking, Self.  You might be silly, but at least you are entertaining.''

The other Christina looked sheepish.  ``Actually... umm, I just ran out of script.  The dream was supposed to have ended just now, so I don't have anything left to say.''

Christina rolled her eyes.  ``Must I do everything myself?  Okay, hmm...''  She got up and turned to face the hero fragments.  ``Come back together, all of you!''  The pieces flew back together, but continued to laugh.   She snapped a finger.  ``Villians!''  A host of villains then appeared, from the Puzzle Master to the Soul Eater.  ``Attack!''  she ordered, and they charged after the heros, who immediately stopped laughing and started to defend themselves.

They easily repelled the villains.  Christina shook her head.  ``No, no, NO!'' she shouted, as the scene froze.  ``You all are doing things all wrong.  For one thing,'' she said, pointing to Lord Voldemort, who was noticeable as the shortest of the rest.  ``Your twelve years old, you shouldn't even be here!''  He disappeared.  ``Now, as for the rest of you... start working with each other!  For example, Soul Eater, you really should be teaming up with the Snake -- he can hold the hero down, and you can pluck out his soul.  And Puzzle Master... for crying out loud, stop holding up your iron puzzle and demanding that the heros solve it and start hitting them with it!''  She went from villain to villain offering further instructions, and then said,  ``Okay, resume everyone!''

The battle started over, and this time the villains did much better.  Many heros started to scream as they were cut into pieces or had their souls eaten.  Eventually, all of them were quiet.

Christina thought to herself.  ``No... that still isn't really want I wanted to see.  I know!  Mark, Homer, appear!''

The two of them appeared in front of her.

``Now,'' she giggled, ``take off your clothes.''  They did so.  ``Okay,'' she continued to command, ``Now \emph{fight}!''

They turned to each other, and started wrestling.  Christina watched this for some time, and then said.  ``Okay, that doesn't look nearly painful enough.  Get some swords already.''  Suddenly, swords appeared in their hands, and there were loud clangs as they clashed against each other.

``Yes!  25,000 words!'' Christina shouted in triumph.

Mark and Homer looked at her.  Christina shrugged.  ``I have no idea where that came from either.  Resume fighting!''

They did so, and Homer cut off Mark's sword arm.  Mark winced in pain, and then screamed as Homer proceeded to chop up him.  ``Hehe,''  Christina giggled.  ``Okay, okay, come back together now and start fighting again.''

They continued to fight like this for some time, with one occasionally dealing a painful series of mortal blows to the other followed by the other resurrecting and starting to fight again.  Eventually the two of them turned to Christina and said,  ``Must we keep doing this?  We're starting to get tired!  Not to mention the fact that it \emph{really hurts}.''

``Oh, all right,'' Christina replied.  ``I guess I should be waking up sometime soon now anyway.''

``Thank you,'' Homer said.

``Oh, you shouldn't be thanking me,'' Christina replied.  ``It's the real Homer who should be grateful that I took out my rage on his dream image rather than the real thing!  Anyway, good bye now.''

The dream started to fade.

\timeskip

%@-node:gcross.20081117194405.2:A silly dream
%@+node:gcross.20081117194405.3:Christina wakes up
Christina woke smiling.  That dream was very therapeutic, she thought to herself.  Mentally, she felt much better.

Unfortunately, she then remebered one of the reasons that she really hadn't wanted to wake up.  She moaned as the full hangover started to sink in.  She ran to the privy in the back.  After spending some time there, she returned to her bed, drank some water and forced down some dried fruit, and lay there for a while.  It was a good thing that she didn't have to be anywhere any time soon.  It felt very un-hero-like to lie in bed and now take on the day by storm, but then again she wasn't a hero any more, now was she?

Oh, and for that matter, where was she, anyway?  Oh, that's right, the new mission.  Ugh, I'll worry about that later, she thought to herself.

Then another thought occured to her, and she chuckled to herself.  At least now that I'm awake, my monologue is internal once more!

\timeskip
%@-node:gcross.20081117194405.3:Christina wakes up
%@+node:gcross.20081122135542.2:Journeying, part 1
Christina spent an indeterminate amount of time dozing.  The movement of the carriage was actually soothing in a way.  Occasionally she felt it stop as the driver took a break.  She wondered when he was going to sleep.

Eventually, the worst of the hangover was over and she climbed up to the top deck.  Angela was there, and she smiled at her.  ``Good afternoon, Christina!''  she said.

``Ugh, what time is it, anyway?''

``Oh, mid-afternoonish.  You've been in bed for quite a while -- which is not surprising at all!''

``Listen, Angela... thank you.''

``For what?''

``For hiring me to do this job and giving me such a comfortable room to crash in on the way and--''

Angela held up her hand.  ``Nonsense!  I am a business woman, first and foremost.  I wouldn't be doing all of this if I didn't think we could make a tidy profit together.''

``Who else have you raided?''  Christina asked.

``I would love to tell you, but that actually is confidental information.  However, on the bright side I won't be asking you any questions about your own adventures as well.''

Christina chuckled.  ``I suppose that is a fair trade.''

There was a moment of silence, which Angela broke by asking, ``So, who are you favoring to win the Quiddich Cup this year?''

Christina laughed.  ``Oh come on now Angela, it is completely obvious that the Teamsters are going to trounce everyone again like they always have.''

``I don't know about that;  the Canines are doing pretty well this year.''

``The only reason that the Canonies have been getting any attention is simply because people love underdog stories.''

``They're seeker is pretty hot.''

``Yeah, but you need to have more than looks to--''

``No, I mean he seems to have these incredible eagle eyes that let him stalk the sky like a hawk and pluck the snitch from the air.''

``True, but you need more on a team than a good seeker.''

``Not if you have Amarous, though.  In the last game he got the snitch within minutes of the game starting.''

``He got lucky that time!''

``He gets lucky a lot.''

They continued bantering about sports for a while, and eventually moved onto talking about other things.  Their conversation was as incredibly impersonal as Christina's conversations with Mark hadn't been, which was nice.

The conversation had another advantage.  Every once and a while, they would pass another carriage or rider who would stare at Christina as they passed and give an expression of disgust.  When this happened, Angela pretended not to notice and continued the conversation, which in turn distracted Christina from being too bothered by it.

Eventually, they started to approach a town.  ``Where are we?''  Christina asked.

``Townsend,'' Angela replied.

``Already?''

``Well, we were travelling all night!''

``Are we doing that again?''

``No, no, that was just to make sure we got a solid start rather than me having to wait for you to crawl out of bed before we could leave.  Tonight we stay at the Green Dragon Inn.''

``Wait, what?  I though that the Green Dragon in was in Wayton?''

``Oh, you didn't know?  They're actually a chain now.''

``Go figure.''

Angela paid the driver an amount Christina considered to be very handsome, though which made sense given the considerable luxory of the ride.

As they walked through the town to the inn, people would occasionally stop, stare at her for a moment, scowl, and then continue on.  One lady did more than scowl, she actually walked up to Christina, shook her fist, and said, ``You worthless hero!  What are you doing here?  Are you going to bring ruin upon us too.''  Christina gritted her teeth, took a deep breath, and forced herself to ignore the woman as she and Angela continued towards their destination.

When they arrived, the innkeeper looked at Christina and scoffed.  ``Why on earth would I want you to stay here?''

Christina flushed as Angela smiled and tossed the innkeeper a bag.  He looked inside it, pondered for a moment, and although his expression did not change he said, ``Very well.  You may stay here.''

``And we will need a warm meal,''  Angela said.

The innkeeper's scowl deepened, but he nodded and allowed them to enter.

They sat at a table in the corner of the room.  At first no one noticed, but eventually someone looked in her direction and whispered to the person next to him, who looked himself, nodded, and told the person next to him, until soon everyone was staring.  Somebody started to boo, and the rest of the crowd started to jeer as well.

Christina had enough.  She stood and drew her sword.  ``So, which of you has a problem with me again?''  The crowd quickly grew silent for a moment, and then they forced themselves to return to whatever conversation that had been engaging in before.

Christina sat down, feeling only slightly better, and if anything mildly disappointed that nobody had challanged her.

During all of this, Angela had been continuing to eat her meal, but she paused, smiled, and told Christina,  ``Watch your temper, Christina;  I may have enough money to bribe a policeman or two, but it will seriously cut into our profits.''

Christina grumbled and resumed eating.  When they were done, they retired to their separate rooms.  Angela went to bed early, but Christina stayed up for an extra hour to review her math textbook, partly to make sure that she was fully prepared for the challange ahead, but mainly to keep her mind from thinking about other things.

\timeskip
%@-node:gcross.20081122135542.2:Journeying, part 1
%@+node:gmc.20081118194801.2:Journeying, part 2
Christina did not dream that night.  Fortunately, the next morning there were not as many people in the inn, and those who were there were neither inebriated nor energetic enough to jeer her any further.  They ate breakfast, and then made their way to the Greyhound carriage rental store, as clouds gathered above them.

``I hope we don't have a repeat of last night with this guy,'' Christina grumbled.

Angela chuckled.  ``I do apologize for that.  However, I know the man that we are going to be renting today's carriage from is a business man after my own heart, and he will not look twice when money is being offered to him.''

Indeed, the man didn't look twice at Christina, but just looked at the money offered him, nodded, and motioned for them to enter the carriage.  This was not as luxorous as the previous day's by any stretch, but was a merely comfortable one.  Christina was not complaining however -- this was still an incredibly luxorous way to travel by hero standards!

Fortunately, unlike the previous day's carriage, this day they were sitting under shelter rather than in the open.  This had two advantages.  First and most obvious, they did not get wet when it started to rain.  Second, people could not see inside as easily, so Christina did not have to put up with any nastly looks.

They were also much quieter.  Having underwent the obligatory amount of pleasant small talk -- and since it was no longer needed to keep Christina too occupied to notice the looks of the people passing them by -- the riders were disinclined to spend a great deal of time bonding more intensely.  So the two spent most of their time reading.  Angela was reading a recently published novel dramaticizing the known exploits of the Shapeshifter, which seemed to be amusing her since she laughed very frequently at the things that she read inside of it.  Christina found this mildly annoying since she felt that villains did not deserve any kind of acclaim, but people did seem to have the strangest tastes.  It's not like she was one to argue;  she spent most of her time reading through some of her old math books to review for the challenge ahead--and also because she genuinely enjoyed reading them!--but when her brain grew tired she would take breaks to read a little more from her trashy romance novel.  (This is something she would have felt embarassing doing openly around one of the other heros in the Order, so in a way it was nice not to have any of them around during the trip!)

At one point during the trip, Christina started to ask a little more about the mission.  ``So... why the Keeper of Maths?''

``Well... so, while it is true that for your benefit I wanted to make this trip as soon as possible so that you wouldn't have time to thi-- I mean worry about tying up your loose ends until you had more money to work with, another major reason is that I happen to know that the Keeper of Maths has just finagled his way into a fraudulent fortune, which is in the process of getting delivered to his fortress now but will only remain for a few days before he launders it into his various research funds.''

``How does he end up with so much money?''

Angela chuckled, ``Well, in a way he his a business man after my own heart;  it would seem that many people in this land enjoy a technically illegal substance called `tobacco'...''

``\emph{What!}  He's still dealing drugs?  I thought that this time we finally managed to destroy all of his crops!''

``One of his genuises is in having lots of backup plans for when he gets shut down, which is why you all have never been able to completely drive him out of business.''

``Damn `Second Chance' rules!'' Christina cursed, not for the first time.

``Ah, but those are brilliant as well, don't you see?  They keep an entire Order continually employed, after all.  Imagine what would happen to you all if all of the villains one day suddenly vanished?  Do you really think that you would be kept around?  The Order is awefully expensive, after all.''

Christina scowled.  ``That kind of thinking is exactly why I didn't go into business!  Well, that and the love of hacking things into little pieces.  And math.''

``Math?''

``Yeah!  Where else do they have decent math courses?  I mean, it's not like it's practical knowledge or anything, so the only groups of people who really use it are villains trying to prove thta they are clever by guarding their fortresses with and heros who need to crack the puzzles in order to make their way in.''

``So you actually joined the Order to learn more about math?''

``Well... that and to have a chance to kick butt!  I mean, it's really nice to have such a great physical and intellectual challenge all rolled into one; that's part of what called me to the order.  Although the intellectualy challenge turned out to be a little underrated since it was easy to ace all of my courses and it turns out that most villains aren't smart enough to give me more than a mild challenge;  I have high hopes for the Keeper of Maths, though.  That, and...''  Christina dropped off mid-sentence.

``And?''  Angela inquired.

``Nothing,''  Christina replied.  ``So tell me, how did you manage to have such good intelligence on the Keeper of Maths?''

Angela smiled.  ``I'm sorry, but unfortunately I cannot reveal my sources.''

``Fair enough.''  There was silence for a couple of minutes, and then they both returned to reading.

\timeskip
%@-node:gmc.20081118194801.2:Journeying, part 2
%@+node:gcross.20081122135542.3:Journeying, part 3
That night, Angela had Christina wait in the carriage as she negotiated with the innkeeper, and then had the carriage take them directly to the inn so that they would not have to walk through the city.  When they entered the innkeeper took them to a private room where they could eat their meal in peace.

``Thank you,'' Christina told Angela with great sincerity.

Angela smiled and waived off the remark with her hand.  ``Say nothing of it;  after all, I do prefer having you be in the best possible condition for our mission -- and I wasn't kidding about how expensive it is to bribe police!''

Christina laughed.

\timeskip
%@-node:gcross.20081122135542.3:Journeying, part 3
%@+node:gcross.20081122135542.4:Journeying, part 4
The next day went like the previous one, save that the rain was not quite as hard.

That night, rather than eating in the common room or in a private room, Christina and Angela ate in their own room, which this time they shared.  As they did so, they started to discuss their plan for the following day.

``So, here is the map of the route that we will be taking,'' Angela told her.

Christina was surprised.  ``You have amazing intelligence!  How on earth can did you... yeah, I know, you can't tell me.  But still, the people who work for the Keeper of Math are so dedicated to the cause that I am amazed you were able to get anyone inside.''

Angela winked at her.  ``Think outside of the box, and it's amazing what you can pull off.  Anyway, so the nice thing is that the Keeper of Maths thinks very little of his soldiers since to him they are just dumb automatons, so he refuses to let him into his tower.  Instead, he keeps them all concentrated in a perimeter protecting the tower like so.  So once we get past them, there will be no need to fight anyone.''

Christina shrugged.  ``Fair enough;  it's more fun when you get the challenge of taking them all on at once rather than one at a time anyway.''

``Oh, we won't be fighting them.  There is no need for us to create such a scene.  Instead, we shall be taking advantage of the fact that the soldiers watching the gates are eternally bored and susceptible to, shall we say, feminine wiles.''

Christina stood and shouted,  ``NO!  I would rather die in battle then deface myself by seducing my way in!''

Angela laughed.  ``Trust me, Christina.  Listen to my full plan.  I guarantee that you will love it!''

\timeskip
%@-node:gcross.20081122135542.4:Journeying, part 4
%@+node:gcross.20081122135542.5:The attack begins
``Marv, you are right, this is so much nicer than standing around, waiting for some hero to kick our heads in!''  Joe said to Marv.

``Yeah, really!''  Marv replied.  ``I mean, doing guard duty for the Keeper of Maths is every bit as boring as for the Puzzle Master, but at least here we get crossbows and a window facing the entry gate which lets us see invaders coming and shoot them down before they get close!''

``Hey, look at that,'' said Joe, pointing through the window.

They watched as two women approach the gate.  They looked through the window and winked at the guards.  ``Hey, there is our entertainment!''  Marv said, pulling the lever which opened the gate.

``Are you sure that this is a...''  Joe started to say, but Marv cut him off patting him roughly on the back.  ``C'mon man, live a little!''

They heard a knocking on their door, and they let the two women in.  They immediately dived at them and kicked their heads in.

``Darnit!  Not ag--''  Marv cursed as he lost consciousness.

The two men took off their breasts and waved through the window and Christina and Angela walked in.

Christina giggled.  ``Cross-dressing mercenaries!  Who've thought!''

Angela chuckled.  ``Yeah, they come in handy in so many places.  Thanks, boys!''  she shouted through the window.

They approached the tower.  Christina could not stop gawking at it.  ``I have never seen any building built of ivory before, nevermind one so enormous... it looks like it is practically touching the sky!''

``It's one hundred stories tall,''  Angela remarked.  ``Good thing that their elevator will take us most of the way up.''

They approached the door.  ``What do a doughnut and a coffee mug have in common?'' it announced.

Christina groaned.  ``Why do you have to ask something so obvious?  They're homeomorphic!  Everybody knows that.''

``Umm, right,'' Angela replied.

They entered the tower, and found themselves in the lobby.  There were fountains on either side of them, and lovely displays of plants.  ``He really spares no expense, Christina remarked.''

A platform lowered itself down to the floor in front of them.  ``That's the elevator,'' Angela remarked.

They walked into it.  ``What floor?''  It asked.  ``90,''  Christina answered before Angela could say anything. 

``That is not a valid floor,'' the voice replied.  ``Please choose from 2, 3, 5, 7, 11, ...''

``Oh, sorry, then we want floor 379.''

The platform started to rise.

Angela was startled.  ``How did you know that?  The floor numbers here have to be memorized;  I was about to tell you that our intelligence had told us that the ninetieth flor was 379.''

Christina laughed.  ``You might have a mind for business, but I have a mind for math.  It was obvious that the all of the floors are numbered after primes, so I just told it the ninetieth prime.''

Angela nodded.  ``Well done!''  she said.

The platform went up ninety floors, and then stopped.

``All right, this is a high as the elevator will take us without authorization.  We have to grapple our way to the top,'' Angela announced.

``Great, now the fun part begins!''  Christina declared, reaching into her bag.  Angela was expecting to see a grappling hook emergy, but instead she saw...

``Sunglasses?  Umm... do those help you see better?''  she asked.

``Of course not! Don't be silly,''  Christina replied as she put them on.  She then reached into her bag and and removed a grappling hook.  She took a couple of minues to aim, and then fired.  The hook flew to the top floor and caught on.  She started to climb her way up the rope;  the rope had a series of knots, so the ascent was not too difficult.  When she made it to the platform on the top, she reached up to it and pulled herself up.  ``All right, secure yourself,'' she called down to Angela.  Angela tied the rope around herself and grabbed Christina's bag.  Christina then pulled her up to the platform.

As Angela stepped onto it, she said, ``You really are incredibly impressive to be so smart and simultaneously so strong.''

Christina grinned.  ``Hey, what can I say;  this kind of thing is what I live for.''

``And... tell me againg, why the sunglasses?'' Angela asked.

``Oh, just because they look cool.''

``I see,'' Angela replied, not seeing.

They could hear a noise down the hallway, which got louder as they approached it.  Finally, they saw it's cause:  the walls were slamming together at regular intervals.

Christina examed it more closely.  There were several walls, some of which closed in from the sides, some of which closed from the ceiling or the floor.  Oh, and she saw now that there were also spikes at several intervals.

Angela started to get nervous.  ``So, I know that these can be traversed, but I have never been sure how people actually did it.''

``Oh, don't worry Angela.  They close at regular intervals.  We just have to decipher the pattern, and then we can walk on through.''  She continued to stare at it for a few moment.  ``Okay,'' Christina said.  ``Here's the plan:  stand next to me, and we are going to walk through together.  I will tell you to go a certain number of walls forward, to go back, or possibly to wait.  Listen closely, and follow my lead.''

Angela still looked a little nervous, Christina walked next to her and put her arm around her.  ``Don't worry, I will keep you close to make sure you don't end up in one of the deadly walls.  Are you ready?''

``I guess so.''

``Okay, then... three steps forward!'' Christina shouted as she and Angela walked to the third wall.  A moment later, the two walls behind them crashed together.  ``One step back!''  she said, dragging Angela to do the same as spikes shot up where they had been standing a moment ago.

They continued this way for a couple of minutes and finally found themselves on the other side.  Christina laughed.  ``That was fun!  Wasn't that great?'' she said to the pale Angela.

``Umm... yes,'' Angela replied.  ``If only we could do that every single day.  Anyway, let's move on.''

They continued down the hallway and made their way to a door.

``Integrate!'' the door shouted.

``Hmm,'' Christina said, thinking to herself.  ``That actually is a tough one.  This will take me a while, hold on,'' she said taking out some paper and scribbling notes.  ``No, integration by parts won't get us anywhere... I suppose I could complete the square... shoot, no, the middle coefficient is off.  Hmm...''

A few minutes later, a new voice appeared behind them.  It was that of a young girl singing.  ``One, two, three, you can't hit me!  One jump back as spikes attack!  Four and five, I do a jive!'' the girl sang, as she systematically made her way through the crashing walls.

Finally, she emerged on the other side.  ``Oh, hi, who are you?'' she asked.

``We're here to visit your father,'' Angela replied.  Christina looked up, and asked,  ``Oh, that's the Keeper of Math's daughter.''

Angela leaned down to her.  ``Yes.  In fact, I bet she could be convinced to open the door for us!''

Christina reached up, grabbed Angela shirt and pulled her close.  ``No, you are not allowed to hurt the girl! Besides, I've almost got this...''

Angela laughed.  ``Why would I do that?''

``Why are you whispering to each other?'' the girl asked.

Angela turned to the girl, ``Well, my friend here is very, very smart, and she is trying to open the door for us.  I told her, though, that maybe you could do it for us.''

The girl's face turned pale and she started to back away.  ``No,  the last time I did that someone hurt my dad!''

Angela shrugged.  ``You don't have to lie.  If you aren't smart enough to solve the problem and let us in, we won't hold it against you.  After all, Christina here is really smart, so I'm sure she'll figure it out eventually.''

``Wait, no, I'm really smart!'' the girl cried.

Angela laughed.  ``Yeah, right!''

``No, I am!  Dad says that I'm a \emph{genius}.''

``He just tells you that because you're his daughter.  But you know, since you aren't smart enough to let us through, I guess I'll just have to hope that she can figure it out, since she really is smart.''

``I've almost got it!'' Christina said.

``No!'' the little girl cried.  ``I am smart!  I'll show you!''  She ran up to the door and wrote something on it.  The door swung open.  ``See!''  she turned to Angela and said, proudly.

Angela clapped with delight.  ``Well done!  You really are much smarter than my friend here.''

``Hey!''  Christina shouted.  ``I almost had it!''

``Told you so!''  the girl said.  She turned around and ran into the room.

Christina grumbled as she put her paper away.  ``I nearly had it.''

``I know, I just figured that there was no point in wasting time.''  Angela replied, laughing.  ``Anyway, now for the snake pit.  Are you sure you are up to this?''

Christina laughed.  ``Of course I am!  Every since the great hero Indiana Jones's notiorious snakeaphobia, they've made us all take mandatory snake training courses so fear of snakes is a thing of the past.  C'mon, let's go.''

They walked into the next room.  There was a rope hanging in the middle, over a pit filled with...

Christina cried out and ran out of the room back into the hallway.  Alarmed, Angela ran over to her.  ``Christina, what's wrong?''

Christina spoke to her accusingly.  ``You said that there was going to be a pit full of snakes.  You said absolutely nothing about spiders!''

``Yes, it would seem that my intelligence was wrong about this... he must have changed it since my last report.  Is this going to be a problem?''

``Is this going to be a problem???  I hate spiders.  The thought of them crawling on me just...'' she shivered.

Angela took deep breath.  ``Okay, I was prepared for this possibility.''  She reached into her own bag and took out a blindfold and a pair of earplugs.  ``First, put on this blindfold.''

``But they'll still be there!'' Angela shrieked.  ``I can't go back in.''

``Trust me on this one.  Put on the blindfold.''  Angela did so.  ``Now what I want you to do is put on the earplugs, reach for the pole in front of you, and then step on the platform.  Hold yourself very tightly onto the pole and you'll be fine.''

``What pole?  What platform?''  Angela asked, confused.

``Just put on the earplugs and feel for the pole.  It will be right in front of you.  Now, when you feel a drop, let go and step off of the platform, and then you can remove your earplugs.''

Angela inserted the earplugs.  She was amazed;  the noise of the crushers behind her was now completely gone!

Skeptically, she reached in front of her.  To her amazement, there was a pole there!  How on earth, she wondered to herself.  She took a step forward and to her surprise felt that there was a platform there!  She stepped onto it and, per her instructions, held herself very closely to the pole.

She felt the pole move a little, and she responded by gripping it even more tightly.  After a couple of moments, she started to wonder when they were going to be entering the room, when she felt the platform drop.  As instructed, she let go and stepped off and removed her earplugs.  She heard a slight whisper in front of her, and then Angela said,  ``Okay, take off your blindfold.''

I wonder what that was supposed to have accomplished, Christina said to herself as she took off the blindfold.  She simultaneously realized two things.  First, that the crushers were no longer audible, and second that they were now facing a completely different door -- this time, one made of wood.

She looked behind her, and saw the put, and across from that the large metal door closing behind them.

She turned to Angela.  ``How on earth...''

Angela smiled and raised her hand to cut her off.  ``Trade secret,'' she replied.

Christina was mystified, but she figured there would be more time to think about this later.  Now they were at the final door and all that they had to do was unlock it and they'd be in!

She reached into her pocket for her lock-pick.  Then into her other pocket.  Then she rummaged frantically through her bag,  ``Oh no way, I definitely packed my lock-pick this time...''

Angela laughed.  ``Don't worry, I brought a spare just in case.''

Christina stopped and looked up.  ``Really?''  She grinned.  ``Heh, we make a good team, you and I, don't we?''

Angela winked.  ``Yup, that's why I hired you.  Let's go see what the Keeper of Maths has to say for himself now, shall we?''

She unlocked the door, and they both walked inside.

\timeskip
%@-node:gcross.20081122135542.5:The attack begins
%@+node:gcross.20081122135542.6:Discussion with the Keeper of Maths
``Ah, Christina, I was expecting you,'' the Keeper of Maths announced, sitting at his desk with his daughter sitting on the desk in front of him.

``What!'' Christina shouted, turning to Angela and looking at her accusingly.  ``What are you pulling on me here?''

Angela looked confused.  ``That... makes no sense.''

The Keeper of Maths laughed.  ``I knew that after the Order threw you out, that you would come back to me again.''

Angela was now ever more confused.  She turned to Christina, who was flushing.  ``Umm... you've been here before?'' she asked.

Christina took a deep breath.  ``When I was younger I applied for a scholarship to study here.''

``What?  I got the impression that you always wanted to be a hero?''

``No... not quite.  At first, I was dreaming of coming to the Keeper of Maths and learning everything that I could from him.  Of course, at the time I was too young to appreciate the ramifications of this...''  She turned to the Keeper of Maths and glared.  ``And then you rejected my application!''

The Keeper shrugged.  ``Guilty as charged,'' he replied gently.  ``It was a mistake that I have long regretted.''

Christina's eyes widened.  ``Really?''

``Oh yeah, I have heard the stories of you, Christina, and was filled with regret and how deeply unappreciated you were by the people for whom you were working.''

``Well, anyway, it's too late now!  We are here to recover your ill-earned drug money.''

``What drug money?'' he asked, surprised.  ``This is all that I have,'' he said, walking over and opening his vault.  There was very little inside.  ``I suppose you could take what I have, if you want, since it's not like it will last me very long, anyway;  it is incredibly expensive to maintain this tower, after all,'' he sighed.

``You... wait... you aren't dealing drugs?''  Christina turned to Angela and stared at her accusingly.  Angela started to reply, but the Keeper of Maths started again, and Christina turned to face him.  ``I learned my lesson before when that horrid hero came her and threatened my daughter, and resolved that I would never make that mistake again.  It has been hard times, but I do not regret it.  Christina... I know that you have been very hurt.  I was expecting you to come back to me, which is why I replaced the snake pit with a spider pit to give myself some additional protection.  However, it would seem that once again I underestimated you.  Please...  I don't know how I will be able to pay you given my lack of funds, but would you consider working for me?  We could use a mind like yours here, advancing the cause of mathematics.''

Christina was silent.  ``I...'' she stammered.

``As touching as this re-union is,'' Angela interrupted.  ``I was wondering, Christina, if you noticed anything funny about the books on the bookself.''

Christina was brought back to her senses, and looked at the bookshelf.  She turned and glared at the Keeper of Maths, ``How dare you put a volume of Newton and one of Leibniz side by side!  The two men hated each other in life;  they'd be rolling in their graves if they knew that...''

``The \emph{third} shelf,'' she interrupted again.

Christina looked closely, and furrowed her brow.  ``Actually, that is quite an impressive collection there!  How on earth did you get an original volume of Euler--''

``While that is indeed interesting, I was thinking along the lines of the fourth book from the right.''

``Why?  There's absolutely nothing noteable about it, though it looks slightly more worn than... Doh!'' she said, smacking her head.  Had she really forgotten all of her training so quickly?  She walked up to the shelf and pulled on the book.  The shelf responded by swinging open, revealing a small room with a single bag.

``I can't belive I missed that,'' she grumbled aloud.  ``It was so obvious!''  She walked into the room, and looked into the bag.  It was an infinite bag of holding;  there were several rooms full of treasure inside!  She turned to the Keeper of Maths and glared at him.  ``You lied to me!  You are dealing drugs, you evil man!''

The Keeper's daughter turned and looked accusingly at him.  ``Daddy... you told Mom that you stopped being evil!''

``I...'' the Keeper started to reply, flummoxed.  Attempting to change the subject, he asked Christina, ``How on earth was the lever obvious?''

``Oh, it wouldn't be obvious to someone without the proper training;  it's just that we heros have long been trained in secret lever detection, ever since the great hero Sherlock Holmes was so successful in using it to fight villains a couple of centuries ago...''  Christina turned to Angela, and continued, ``But that doesn't explain how \emph{you} were able to figure it out.''

Angela shrugged, and procceeded to ignore what Christina just said by replying, ``Well done, Christina;  though you needed a little bit of prodding at the end.  For your reward, please take a couple of handfuls of treasure from the bag;  that should be enough to give you food and rent for a couple of years, plenty of time for you to get back on your feet.  The rest, however, will go to me.''

``What!'' Christina shouted, startled.  ``That was not the deal!''

Angela quickly reached over to the daughter and puller her close as she simultaneously yanked a dagger from her pocket and put it at her throat.  ``No!''  the Keeper shouted.  ``Please, not my daughter!''

The girl was to afraid to move at all, but her face grew pale and a tear started to flow down her cheek.

Christina froze.  ``You wouldn't,'' she said to Angela, astonished.

Angela shrugged.  ``Maybe I would, maybe I wouldn't.  It is irrelevant what I am willing to do since you are not willing to take the risk.''

Christina slumped.  Curse her, she was right!

``What do you want,'' the Keeper asked, pained.

Angela laughed.  ``Just all your treasure.  Oh, Christina, before you give the bag to me, please take out a couple of handfuls for yourself.''

Christina simply threw her the bag.  ``I refuse to benefit from a child being harmed.''

The bag sat on the floor in front of Angela.  She kept the dagger at the child's throat as she let go and picked up the bag with her other hand.  She balanced it againster her, took out several handfuls of treasure and tossed them onto the floor.  ``Well, if you change your mind I am leaving a share for you.  If you turn it down, though, then don't blame me when you no longer have a place at which to stay.''

``Is that all you want?  Fine,  take it, just leave my daughter alone, please.''  Another man might have stopped with that, but since he was the Keeper of Maths he could not stop himself remaking out of curiousity, ``I still can't figure out, though, how you that stash was there... no one knows about it;  only the furniture in the room has only seen me use it.''

``Ah, and there was your problem,'' Angela replied with mirth.  Suddenly, her lower body from the waist down seemed to melt into a colorless fluid, and then reshaped itself into the legs of a chair.  ``The furniture \emph{did} see your stash!''

``You're the shapeshifter!''  Christina said in shock.

``Way to state the obvious, Christina.''  She winked.  ``Now Keeper, please go ahead and shut Christina in that room there while I make my mistake.  It's up to you whether you decide to let her out again.''

The Keeper got up and closed the shelf, and Christina was plummeted into darkness.

\timeskip
%@-node:gcross.20081122135542.6:Discussion with the Keeper of Maths
%@+node:gcross.20081122135542.7:Departing the Keeper
Christina waited for what felt like an eternity before the shelves opened again.  The Keeper was standing in front of her, with his daughter crying and clinging to him.

``I assume that she is gone?''  Christina asked.

``Yes, she transformed into some kind of flying creature and left through the window -- assuming it is a she, that is,'' the Keeper replied.

Christina ran to the window and looked out.  She saw a pair of wings in the distance, getting smaller as it grew more distant.

``Thank you, by the way,'' the Keeper said to her.  She turned to face him as he continued, ``I deeply appeciate that you were not willing to risk the life of my daughter.  Please, go ahead and take this money that the creature has left for you on the floor as my token of thanks.''

Christina's face darkened.  ``That won't be necessary,'' she replied.  ``I plan on recovering the full treasure from the Shapeshifter as soon as I can.''  She returned to looking outside the window.  ``If only I had some way of catching up to her...''

``Hmm... if that is all you want, then I might have something that can help you,'' the Keeper replied.  He walked to one of his cabinets (an awkward process given his daughter's tight grip) and removed a strange device of metal.  ``I was trying to figure out what to do with this thing... One of the disadvantages of giving my researchers tenure is that I technically cannot force them to work on particular projects, and so some of them choose to work on distastefully `applied' projects.''  He gestured to the device.  ``This device burns alcohol and produces a jet of air.  It can be mounted on a pair of wings, and theoretically could allow someone to fly through the air.''

``Theoretically?''

``Nobody has been stupid enough to actually try it out.''

Christina grinned.  ``I'd be glad to be the first!''

``Hmm... the problem is that I doubt that this thing can be flown by someone who is unskilled.  The way that the wings operate is that there are two ropes, and pulling on one or the other causes it to fly in that direction.  There are another couple of ropes that bend the front and the back of the wings that should cause it to adjust it's altitude.  You would need to be skilled at operating these ropes to have a chance of surviving, and --''

``No problem!  I actualy have experience with a similar device, so this shouldn't be too much more trouble.''

The Keeper's eyebrows were raised.  ``Interesting.  Well, your life is your own.  Take the risk if you wish.''

``Thank you,'' she replied, and started to put on the equipment.  She stopped, and walked over to the crying girl.  She touched the girls head, and the girl looked up at her.  Christina reached into a pocket, pulled out a card, and gave it to the girl.  ``When I was your age, I was often afraid too.  Boys would pick on me for being the nerdy one in school, and I was often hurt.  However, I signed up for martial arts classes from the Order, and they taught me to be strong so that they couldn't pick on me any more.  I wanted to be even more tough, so eventually I ended up signing up to be trained as a hero myself.  It was hard, and the Order has not been kind to me, but they did make me strong, and now there is nothing on earth that I fear.  Well, except for spiders.''

The girl couldn't help giggling.  ``I'm not afraid of spiders!''

Christina smiled.  ``Well, then when you're grown up you'll have even less to fear than me.  Anyway, just keep it in mind.''

The Keeper was silent as Christina mounted the device and her wings.  She walked over to the window.

``Christina... my offer remains open, if you ever want to return.''

She turned to him.  ``C'mon, Keeper!  I would love to, but I just cannot stand the idea of being funded by drug money.  You've got to be able to find \emph{some} other kind of funding.  Maybe you could start getting your researchers to make more devices like this and then sell them or something.''

``But the applied sciences are so impure!''

``The might be, but then at least you won't be constantly fighting people.''

``Yeah, that's true...'' he said, resigned.  He looked down at his daughter.  ``You know... maybe I have been putting pure math a little too high in my life.  Well, farewell, Christina.''

Christina jumped.

\timeskip
%@-node:gcross.20081122135542.7:Departing the Keeper
%@-node:gcross.20081108185724.12:Chapter 3: The Keeper of Maths
%@+node:gcross.20081119221421.2:Chapter 4
\chapter{The Shapeshifter}
%@-node:gcross.20081119221421.2:Chapter 4
%@+node:gcross.20081111232036.5:Appendix: The Reward
\appendix{}
%@+node:gcross.20081111232036.6:NewHeadline
%@-node:gcross.20081111232036.6:NewHeadline
%@-node:gcross.20081111232036.5:Appendix: The Reward
%@-node:gcross.20081101122204.2:Story
%@-others

\end{document}
%@-node:gcross.20081101122204.4:@thin story.tex
%@-leo
